---
title: '"L2_dataAnalysis_CDCRdata_Nutrient_AllDist_Calc_CoarseEnv"'
author: "laís_petri"
date: "2025-03-27"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
rm(list = ls())
started <- Sys.time()
```

```{r package and directory, echo=FALSE}
## data wrangling + plots
library(tidyverse) 
library(scales)
library(patchwork)
## color blind discrete colors
library(pals) 
## arrange plots
library(cowplot)
```

Folders
```{r}
workingdir <- getwd()
datain <- file.path(workingdir, "parameters/CoarseEnv")
ldatain <- file.path(workingdir, "parameters/CoarseEnv_FieldsAB")
```

General objects   
```{r}
#trick to plot 9 before all other treatments
order_levels <- c(9, 1, 2, 3, 4, 5, 6, 7, 8)
ntrtLong_levels <- c("0 + None", "0 + All", "1 + All", "2 + All", "3.4 + All", "5.4 + All", "9.5 + All", "17 + All", "27.2 + All")
```

Importing datasets: summary stats
- live biomass
```{r}
## All years
# Intact model results
parameters0_NoDist <- read_csv(file.path(datain,"NoDist_CoarseEnv_ParametersValues.csv")) %>% 
    mutate(exp = 1,
           dur = 1) # 1=All years, 2 = Minus5y
glimpse(parameters0_NoDist)

# Disturbed model results
parameters0_Dist <- read_csv(file.path(datain,"Dist_CoarseEnv_ParametersValues.csv")) %>% 
    mutate(exp = 2,
           dur = 1)
glimpse(parameters0_Dist)

## Minus5y
# Intact model results
parameters0_NoDist2 <- read_csv(file.path(datain,"NoDistMinus5y_CoarseEnv_ParametersValues.csv")) %>% 
    mutate(exp = 1,
           dur = 2)
glimpse(parameters0_NoDist2)

# Disturbed model results
parameters0_Dist2 <- read_csv(file.path(datain,"DistMinus5y_CoarseEnv_ParametersValues.csv")) %>% 
    mutate(exp = 2,
           dur = 2)
glimpse(parameters0_Dist2)

# merging all datasets
parameters_All <- rbind(parameters0_NoDist,parameters0_Dist,parameters0_NoDist2,parameters0_Dist2) 
```

- dead biomass
```{r}
## All years
# Intact model results
parameters0_NoDist <- read_csv(file.path(ldatain,"NoDist_Litter_FieldsAB_CoarseEnv_ParametersValues.csv")) %>% 
    mutate(exp = 1,
           dur = 1) # 1=All years, 2 = Minus5y
glimpse(parameters0_NoDist)

# Disturbed model results
parameters0_Dist <- read_csv(file.path(ldatain,"Dist_Litter_FieldsAB_CoarseEnv_ParametersValues.csv")) %>% 
    mutate(exp = 2,
           dur = 1)
glimpse(parameters0_Dist)

## Minus5y
# Intact model results
parameters0_NoDist2 <- read_csv(file.path(ldatain,"NoDist_Litter_FieldsAB_Minus5y_CoarseEnv_ParametersValues.csv")) %>% 
    mutate(exp = 1,
           dur = 2)
glimpse(parameters0_NoDist2)

# Disturbed model results
parameters0_Dist2 <- read_csv(file.path(ldatain,"Dist_Litter_FieldsAB_Minus5y_CoarseEnv_ParametersValues.csv")) %>% 
    mutate(exp = 2,
           dur = 2)
glimpse(parameters0_Dist2)

# merging all datasets
lparameters_All <- rbind(parameters0_NoDist,parameters0_Dist,parameters0_NoDist2,parameters0_Dist2) 
```


Importing datasets: values from posterior distributions
- live biomass
```{r}
## All years
# Intact model results
parametersPost_NoDist <- read_csv(file.path(datain,"NoDist_CoarseEnv_parameters.csv"))
glimpse(parametersPost_NoDist)

# Disturbed model results
parametersPost_Dist <- read_csv(file.path(datain,"Dist_CoarseEnv_parameters.csv"))
glimpse(parametersPost_Dist)

## Minus5y
# Intact model results
parametersPost_NoDist2 <- read_csv(file.path(datain,"NoDistMinus5y_CoarseEnv_parameters.csv"))
glimpse(parametersPost_NoDist2)

# Disturbed model results
parametersPost_Dist2 <- read_csv(file.path(datain,"DistMinus5y_CoarseEnv_parameters.csv"))
glimpse(parametersPost_Dist2)
```

- dead biomass
```{r}
## All years
# Intact model results
lparametersPost_NoDist <- read_csv(file.path(ldatain,"NoDist_Litter_FieldsAB_CoarseEnv_parameters.csv"))
glimpse(lparametersPost_NoDist)

# Disturbed model results
lparametersPost_Dist <- read_csv(file.path(ldatain,"Dist_Litter_FieldsAB_CoarseEnv_parameters.csv"))
glimpse(lparametersPost_Dist)

## Minus5y
# Intact model results
lparametersPost_NoDist2 <- read_csv(file.path(ldatain,"NoDist_Litter_FieldsAB_Minus5y_CoarseEnv_parameters.csv"))
glimpse(lparametersPost_NoDist2)

# Disturbed model results
lparametersPost_Dist2 <- read_csv(file.path(ldatain,"Dist_Litter_FieldsAB_Minus5y_CoarseEnv_parameters.csv"))
glimpse(lparametersPost_Dist2)
```

Importing datasets: predictions of effect vs ntrt quantity
- live biomass
```{r}
## All years
# Preciptation
precip.pred <- read_csv(file.path(workingdir,"parameters/CoarseEnv_Slopes/abg/precipData_ParametersValues.csv")) %>% 
  mutate(alpha=2,
         dur = 1)
glimpse(precip.pred)

# temperature
temp.pred <- read_csv(file.path(workingdir,"parameters/CoarseEnv_Slopes/abg/tempData_ParametersValues.csv")) %>% 
  mutate(alpha=3,
         dur = 1)
glimpse(temp.pred)

## Minus5y
# Preciptation
precip.pred2 <- read_csv(file.path(workingdir,"parameters/CoarseEnv_Slopes/abgMinus5y/precipData_ParametersValues.csv")) %>% 
  mutate(alpha=2,
         dur = 2)
glimpse(precip.pred2)

# temperature
temp.pred2 <- read_csv(file.path(workingdir,"parameters/CoarseEnv_Slopes/abgMinus5y/tempData_ParametersValues.csv")) %>% 
  mutate(alpha=3,
         dur = 2)
glimpse(temp.pred2)
```

- dead biomass
```{r}
## All years
# Preciptation
lprecip.pred <- read_csv(file.path(workingdir,"parameters/CoarseEnv_FieldsAB_Slopes/litter/precipData_ParametersValues.csv")) %>% 
  mutate(alpha=2,
         dur = 1)
glimpse(lprecip.pred)

# temperature
ltemp.pred <- read_csv(file.path(workingdir,"parameters/CoarseEnv_FieldsAB_Slopes/litter/tempData_ParametersValues.csv")) %>% 
  mutate(alpha=3,
         dur = 1)
glimpse(ltemp.pred)

## Minus5y
# Preciptation
lprecip.pred2 <- read_csv(file.path(workingdir,"parameters/CoarseEnv_FieldsAB_Slopes/litterMinus5y/precipData_ParametersValues.csv")) %>% 
  mutate(alpha=2,
         dur = 2)
glimpse(lprecip.pred2)

# temperature
ltemp.pred2 <- read_csv(file.path(workingdir,"parameters/CoarseEnv_FieldsAB_Slopes/litterMinus5y/tempData_ParametersValues.csv")) %>% 
  mutate(alpha=3,
         dur = 2)
glimpse(ltemp.pred2)
```

# Results (Calculations)
## LIVE biomass
### All Years
- Global effects: percent of posterior distribution above 0
```{r}
# TEMPERATURE

# Intact plots
# Extract posterior samples for "mu_a"
mu_a_samplesI <- as.matrix(parametersPost_NoDist)[,"mu_a.star[3]"]

# Calculate the proportion of samples greater than 0
print(paste("Percentage of the posterior distribution above 0 for intact plots:", round(mean(mu_a_samplesI > 0)*100,1)))

# Disturbed plots
# Extract posterior samples for "mu_a"
mu_a_samplesD <- as.matrix(parametersPost_Dist)[,"mu_a.star[3]"]

# Calculate the proportion of samples greater than 0
print(paste("Percentage of the posterior distribution above 0 for disturbed plots:", round(mean(mu_a_samplesD > 0)*100,1)))
```

- Magnitude of effect: Disturbed/Intact of each ntrt trt per environmental variable
```{r}
Alphamodelpar_ratio <- parameters_All %>% 
  filter(grepl("^mu_a_ntrt.star",parameter)) %>% 
  mutate(alpha = rep(1:4,times=36),
         ntrt = factor(rep(1:9,times=4, each=4), levels = order_levels),
         ntrtLong = factor(rep(c("0 + All", "1 + All", "2 + All", "3.4 + All", "5.4 + All", "9.5 + All", "17 + All", "27.2 + All", "0 + None"),times=4, each=4), levels = ntrtLong_levels)) %>% 
  filter(alpha %in% c(2,3)) %>% 
  arrange(alpha, ntrt, ntrtLong, exp) %>%  
  group_by(alpha, ntrt, ntrtLong) %>%
  summarize(statistics_Mean_ratio = round(abs(statistics.Mean[exp == 2]) / abs(statistics.Mean[exp == 1]),2)) %>%
  ungroup() %>% 
  mutate(alpha_name = ifelse(alpha==2, "Precipitation", "Temperature")) %>% 
  select(alpha_name, everything())

Alphamodelpar_ratio
```

- Magnitude of effect: Disturbed/Intact per environmental variable
```{r}
precip.pred %>% 
  filter(grepl("^beta\\[\\d+\\]$",parameter)) %>% 
  mutate(exp = c(1,2)) %>% 
  group_by(alpha) %>% 
  summarise(statistics_Mean_ratio = round(abs(statistics.Mean[exp == 2]) / abs(statistics.Mean[exp == 1]),2))

temp.pred %>% 
  filter(grepl("^beta\\[\\d+\\]$",parameter)) %>% 
  mutate(exp = c(1,2)) %>% 
  group_by(alpha) %>% 
  summarise(statistics_Mean_ratio = round(abs(statistics.Mean[exp == 2]) / abs(statistics.Mean[exp == 1]),2))
```

Raw overall effect of eacn environmental variable on live biomass
```{r}
parameters_All %>% 
  filter(grepl("^mu_a.star\\[\\d+\\]$",parameter),
         dur==1) %>% # coefs for full dataset ony
  mutate(var = rep(c("precip","temp"), times=2)) %>% 
  arrange(var)
```

## DEAD biomass
### All Years
- Global effects: percent of posterior distribution above 0
```{r}
# PRECIPITATION
# Disturbed plots: all years
# Extract posterior samples for "mu_a"
mu_a_samplesD_All <- as.matrix(lparametersPost_Dist)[,"mu_a.star[2]"]

# Calculate the proportion of samples greater than 0
print(paste("Percentage of the posterior distribution above 0 for disturbed plots [all years, precipitation]:", round(mean(mu_a_samplesD_All > 0)*100,1)))

# TEMPERATURE
# Disturbed plots: minus 5y
# Extract posterior samples for "mu_a"
mu_a_samplesD_Minus5y <- as.matrix(lparametersPost_Dist2)[,"mu_a.star[3]"]

# Calculate the proportion of samples greater than 0
print(paste("Percentage of the posterior distribution above 0 for disturbed plots [minus 5y, temperature]:", round(mean(mu_a_samplesD_Minus5y > 0)*100,1)))
```

- Magnitude of effect: Disturbed/Intact of each ntrt trt per environmental variable
```{r}
Alphamodelpar_ratio <- lparameters_All %>% 
  filter(grepl("^mu_a_ntrt.star",parameter)) %>% 
  mutate(alpha = rep(1:4,times=36),
         ntrt = factor(rep(1:9,times=4, each=4), levels = order_levels),
         ntrtLong = factor(rep(c("0 + All", "1 + All", "2 + All", "3.4 + All", "5.4 + All", "9.5 + All", "17 + All", "27.2 + All", "0 + None"),times=4, each=4), levels = ntrtLong_levels)) %>% 
  filter(alpha %in% c(2,3)) %>% 
  arrange(alpha, ntrt, ntrtLong, exp) %>%  
  group_by(alpha, ntrt, ntrtLong) %>%
  summarize(statistics_Mean_ratio = round(abs(statistics.Mean[exp == 2]) / abs(statistics.Mean[exp == 1]),2)) %>%
  ungroup() %>% 
  mutate(alpha_name = ifelse(alpha==2, "Precipitation", "Temperature")) %>% 
  select(alpha_name, everything())

Alphamodelpar_ratio
```

- Magnitude of effect: Intact/Disturbed per environmental variable
```{r}
# all years
lprecip.pred %>% 
  filter(grepl("^beta\\[\\d+\\]$",parameter)) %>% 
  mutate(exp = c(1,2)) %>% 
  group_by(alpha) %>% 
  summarise(statistics_Mean_ratio = round(abs(statistics.Mean[exp == 1]) / abs(statistics.Mean[exp == 2]),2))

ltemp.pred %>% 
  filter(grepl("^beta\\[\\d+\\]$",parameter)) %>% 
  mutate(exp = c(1,2)) %>% 
  group_by(alpha) %>% 
  summarise(statistics_Mean_ratio = round(abs(statistics.Mean[exp == 1]) / abs(statistics.Mean[exp == 2]),2))

# minus 5y
lprecip.pred2 %>% 
  filter(grepl("^beta\\[\\d+\\]$",parameter)) %>% 
  mutate(exp = c(1,2)) %>% 
  group_by(alpha) %>% 
  summarise(statistics_Mean_ratio = round(abs(statistics.Mean[exp == 1]) / abs(statistics.Mean[exp == 2]),2))

ltemp.pred2 %>% 
  filter(grepl("^beta\\[\\d+\\]$",parameter)) %>% 
  mutate(exp = c(1,2)) %>% 
  group_by(alpha) %>% 
  summarise(statistics_Mean_ratio = round(abs(statistics.Mean[exp == 1]) / abs(statistics.Mean[exp == 2]),2))
```

Raw overall effect of each environmental variable on dead biomass
```{r}
lparameters_All %>% 
  filter(grepl("^mu_a.star\\[\\d+\\]$",parameter),
         dur==1) %>% # coefs for full dataset ony
  mutate(var = rep(c("precip","temp"), times=2)) %>% 
  arrange(var)
```

