---
title: "L0_Weather_dataWrangling"
author: "laís petri"
date: "2024-01-24"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r package and directory, echo=FALSE}
#import excel sheet
# require(readxl)
#data wrangling and plot
require(tidyverse)
## color blind discrete colors
require(pals)
```

Paths to import files, and export outputs
```{r}
workingdir <- getwd()
datain <- file.path(workingdir, "data/L0")
dataout <- file.path(workingdir, "data/L1")
graph.wd <- file.path(workingdir, "figures")
```

Defining colors
```{r}
fieldcolor<-as.vector(alphabet(3))
# sitecolor2<-c("#F0A0FF","#cce3f8")
# mocolor<-as.vector(alphabet2(3))
# mocolor2 <- c("#DD9EFE","#AA0DFE","#ADCDFE","#3283FE","#CEC19E","#85660D")
```

Defining graph size font
```{r}
graph.size <- 12
title.size <- 14
```

## upload data
```{r}
weatherData <- as_tibble(read_csv(file.path(datain,'e080_Daily climate summary.csv')))
glimpse(weatherData) # daily values of Min and Max Temp, and Precip

pdsi <- as_tibble(read_csv(file.path(datain,'PDSI/gridMET/monthly_pdsi.csv')))
glimpse(pdsi)
```

## data exploration
```{r}
weatherData %>% 
  select(Year,Month) %>% distinct() %>% 
  ungroup() %>% 
  group_by(Year) %>%
  summarise(MonthCount = n_distinct(Month)) %>%
  ungroup() %>% filter(MonthCount!=12)

#range of years for PlantComm data: 1982 2021

# therefore, the only missing year is 2007, I can exclude 1962 and 2023 to not give trouble when analyzing data
# but, now that I am using data until 2021, I will fill in the missing month with the average values for month 2 across the entire sequence (1963-2022). I am doing this because I couldn't figure out how to fill in missing data given the structure in which the ppt and temp are read by the model 

weatherData <- weatherData %>% 
  filter(Year > 1962,
         Year < 2023)
```

## calculating monthly averages
```{r}
#for calculations, following https://www.nrcs.usda.gov/wps/portal/wcc/home/climateSupport/wetlandsClimateTables/exampleAndDefinitions

weatherDataMonth <- weatherData %>% 
  group_by(Year, Month) %>% 
  summarise(MaxTemp_C=mean(MaxTemp_C),
            MinTemp_C=mean(MinTemp_C),
            Precip_mm=sum(Precip_mm)) %>% 
  ungroup()

Month2 <- weatherDataMonth %>% 
  group_by(Month) %>% 
  summarise(MaxTemp_C=mean(MaxTemp_C),
            MinTemp_C=mean(MinTemp_C),
            Precip_mm=mean(Precip_mm)) %>% 
  ungroup() %>% 
  filter(Month==2) %>% 
  as.vector

## creating row with missing data
dataframe <- c(Year = 2007,
               Month = 2, 
               MaxTemp_C = Month2[["MaxTemp_C"]],
               MinTemp_C = Month2[["MinTemp_C"]],
               Precip_mm = Month2[["Precip_mm"]])

## adding missing data
weatherDataMonth <- weatherDataMonth %>% 
  rbind(dataframe) 

#checking whether my trick worked
weatherDataMonth %>% 
  select(Year,Month) %>% distinct() %>% 
  ungroup() %>% 
  group_by(Year) %>%
  summarise(MonthCount = n_distinct(Month)) %>%
  ungroup() %>% filter(MonthCount!=12)
```

## PDSI
```{r}
pdsi <- pdsi %>% 
  mutate(Year = year(YearMonth),
         Month = month(YearMonth)) %>% 
  select(-YearMonth) %>% 
  rename(PDSI = Monthly_PDSI)

weatherDataMonth <- weatherDataMonth %>% left_join(pdsi) 

glimpse(weatherDataMonth)
```


### exporting file
```{r eval=FALSE, include=FALSE}
#exporting data
weatherDataMonth %>% 
  glimpse() %>% 
  write_csv(file.path(dataout,"da_weather_020625.csv"))

```

## data exploration
```{r}
# not the best graphs, but we can have an idea that there is variability, which is good!
weatherDataMonth %>% 
ggplot(aes(y=Precip_mm,x=Month, color=as.factor(Year)))+
  geom_line()+
  geom_point(size=5,alpha=1)+
  # scale_color_manual(values=sitecolor, name="sites")+
  scale_x_continuous(breaks = seq(min(weatherData$Month), max(weatherData$Month), by = 1)) +
  xlab("Month")+
  ylab("Total yearly precipitation (mm)")+
  # facet_wrap(~Year)+
  theme_bw()+
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        legend.position = "bottom",
        legend.text=element_text(size=12),
        legend.title=element_text(size=13),
        legend.margin=margin(0,0,0,0),
        legend.box.margin=margin(-5,-5,-5,-5),
        axis.text = element_text(size = graph.size),
        # axis.text.x = element_text(size = graph.size-5),
        axis.title = element_text(size = title.size),
        # axis.title.x = element_blank(),
        strip.text.y = element_text(size = graph.size))+ 
    guides(colour = guide_legend(nrow = 1))

weatherDataMonth %>% 
ggplot(aes(y=MinTemp_C,x=Month, color=as.factor(Year)))+
  geom_line()+
  geom_point(size=5,alpha=1)+
  # scale_color_manual(values=sitecolor, name="sites")+
  scale_x_continuous(breaks = seq(min(weatherData$Month), max(weatherData$Month), by = 1)) +
  xlab("Month")+
  ylab("Average min monthly temperature (C)")+
  # facet_wrap(~Year)+
  theme_bw()+
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        legend.position = "bottom",
        legend.text=element_text(size=12),
        legend.title=element_text(size=13),
        legend.margin=margin(0,0,0,0),
        legend.box.margin=margin(-5,-5,-5,-5),
        axis.text = element_text(size = graph.size),
        # axis.text.x = element_text(size = graph.size-5),
        axis.title = element_text(size = title.size),
        # axis.title.x = element_blank(),
        strip.text.y = element_text(size = graph.size))+ 
    guides(colour = guide_legend(nrow = 1))

weatherDataMonth %>% 
ggplot(aes(y=MaxTemp_C,x=Month, color=as.factor(Year)))+
  geom_line()+
  geom_point(size=5,alpha=1)+
  # scale_color_manual(values=sitecolor, name="sites")+
  scale_x_continuous(breaks = seq(min(weatherData$Month), max(weatherData$Month), by = 1)) +
  xlab("Month")+
  ylab("Average max monthly temperature (C)")+
  # facet_wrap(~Year)+
  theme_bw()+
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        legend.position = "bottom",
        legend.text=element_text(size=12),
        legend.title=element_text(size=13),
        legend.margin=margin(0,0,0,0),
        legend.box.margin=margin(-5,-5,-5,-5),
        axis.text = element_text(size = graph.size),
        # axis.text.x = element_text(size = graph.size-5),
        axis.title = element_text(size = title.size),
        # axis.title.x = element_blank(),
        strip.text.y = element_text(size = graph.size))+ 
    guides(colour = guide_legend(nrow = 1))


weatherDataMonth %>% 
  filter(!is.na(PDSI)) %>% 
ggplot(aes(y=PDSI,x=Month, color=as.factor(Year)))+
  geom_line()+
  geom_point(size=4,alpha=0.5)+
  # scale_color_manual(values=sitecolor, name="sites")+
  scale_x_continuous(breaks = seq(min(weatherData$Month), max(weatherData$Month), by = 1)) +
  xlab("Month")+
  ylab("PDSI")+
  facet_wrap(~Year)+
  theme_bw()+
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        legend.position = "bottom",
        legend.text=element_text(size=12),
        legend.title=element_text(size=13),
        legend.margin=margin(0,0,0,0),
        legend.box.margin=margin(-5,-5,-5,-5),
        axis.text = element_text(size = graph.size),
        # axis.text.x = element_text(size = graph.size-5),
        axis.title = element_text(size = title.size),
        # axis.title.x = element_blank(),
        strip.text.y = element_text(size = graph.size))+ 
    guides(colour = guide_legend(nrow = 1))

# Precip ~ PDSI
correlation_value <- cor(weatherDataMonth$Precip_mm, weatherDataMonth$PDSI, use = "complete.obs")

weatherDataMonth %>%
  filter(!is.na(PDSI)) %>% 
  ggplot(aes(y = Precip_mm, x = PDSI)) +
  annotate("text", x = Inf, y = Inf, label = sprintf("cor: %.4f", correlation_value), 
           hjust = 4, vjust = 1.5, size = 6) +
  geom_point(shape=19,size=5,alpha=0.5) +
  ylab("Precipitation (mm)")+
  xlab("PDSI")+ 
  theme_classic()+
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        axis.text.y = element_text(size = 25),
        axis.text.x = element_text(size = 25),
        axis.title = element_text(size = 25),
        axis.line = element_line(colour = "black"))

#Max temp
correlation_value <- cor(weatherDataMonth$MaxTemp_C, weatherDataMonth$PDSI, use = "complete.obs")

weatherDataMonth %>%
  filter(!is.na(PDSI)) %>% 
  ggplot(aes(y = MaxTemp_C, x = PDSI)) +
  annotate("text", x = Inf, y = Inf, label = sprintf("cor: %.4f", correlation_value), 
           hjust = 4, vjust = 1.5, size = 6) +
  geom_point(shape=19,size=5,alpha=0.5) +
  ylab("Maximum Temperature")+
  xlab("PDSI")+ 
  theme_classic()+
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        axis.text.y = element_text(size = 25),
        axis.text.x = element_text(size = 25),
        axis.title = element_text(size = 25),
        axis.line = element_line(colour = "black"))

# ggsave(paste0(file.path(graph.wd,"MaxAvgTemp_.png")), plot = last_plot(), width=7, height=5, dpi = 300, units="in")
```


# addition to calculate yearly averages across the most up-to-date chronology
## upload data
```{r}
weatherData <- as_tibble(read_csv(file.path(datain,'e080_Daily climate summary.csv')))
glimpse(weatherData) # daily values of Min and Max Temp, and Precip
```

## get summaries
```{r}
#monthly means
weatherDataMonth <- weatherData %>% 
  mutate(Date = as.Date(Date, "%m/%d/%Y"),
         Month = month(Date), 
         Year = year(Date)) %>% 
  group_by(Year, Month) %>% 
  summarise(MaxTemp_C=mean(MaxTemp_C),
            MinTemp_C=mean(MinTemp_C),
            Precip_mm=sum(Precip_mm)) %>% 
  ungroup() %>% 
  mutate(AvgTemp_C=(MaxTemp_C+MinTemp_C)/2) 

#yearly means
weatherDataYear <- weatherDataMonth %>% 
  group_by(Year) %>% 
  summarise(AvgTemp_C=mean(AvgTemp_C),
            Precip_mm=sum(Precip_mm)) %>% 
  ungroup()

#chronology mean
weatherDataYear %>% 
  summarise(AvgTemp_C_SD=sd(AvgTemp_C),
            AvgTemp_C=mean(AvgTemp_C),
            Precip_mm_SD=sd(Precip_mm),
            Precip_mm=mean(Precip_mm))

# highest and lowest temp (Jan and July)
weatherDataMonth %>% 
  group_by(Year, Month) %>% 
  summarise(AvgTemp_C=mean(AvgTemp_C)) %>% 
  group_by(Month) %>% 
  summarise(AvgTemp_C_SD=sd(AvgTemp_C),
            AvgTemp_C=mean(AvgTemp_C))
```

## plot Max temp ~ Mean temp
```{r}
correlation_value <- cor(weatherDataMonth$MaxTemp_C, weatherDataMonth$AvgTemp_C)

weatherDataMonth %>% 
  filter(Year < 2005) %>% 
ggplot(aes(y = MaxTemp_C, x = AvgTemp_C)) +
  annotate("text", x = Inf, y = Inf, label = sprintf("cor: %.4f", correlation_value), 
           hjust = 4, vjust = 1.5, size = 6) +
  geom_point(shape=19,size=5,alpha=0.5) +
  ylab("Maximum temperature")+
  xlab("Average temperature")+ 
  theme_classic()+
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        axis.text.y = element_text(size = 25),
        axis.text.x = element_text(size = 25),
        axis.title = element_text(size = 25),
        axis.line = element_line(colour = "black"))

ggsave(paste0(file.path(graph.wd,"MaxAvgTemp_MeanTemp.png")), plot = last_plot(), width=7, height=5, dpi = 300, units="in")
```

# correlation between covariates
Correlation between Precip and Temp
```{r}
# All data
## to run this code, I need to import data from models
load(file.path(dataout,"DataModel_CoarseEnv/DataModel_Dist_CoarseEnv.RData"))

clim.matrix.df <- as_tibble(clim.matrix)

fit <- lm(Precip_mm ~ MaxTemp_C, data=clim.matrix.df)
correlation <- cor(clim.matrix.df$Precip_mm,clim.matrix.df$MaxTemp_C)


ggplot(data = clim.matrix.df, aes(y = Precip_mm, x = MaxTemp_C)) +
  stat_function(fun = function(x) predict(fit, newdata = data.frame(MaxTemp_C = x)),
                color = "black", linewidth = 2) +
  annotate(label = sprintf("y = %.3f + %.3f x\nR² = %.2f", coef(fit)[1], coef(fit)[2], summary(fit)$r.squared),
           geom = "text", x = 0, y = 230, size = 5) +
  annotate(label = paste0("cor = ",round(correlation,2)),
           geom = "text", x = 0, y = 205, size = 5) +
  geom_point(shape=19,size=5,alpha=0.5) +
  # xlim(0,1300)+
  ylab("Monthly Precipitation (mm)")+
  xlab(expression("Monthly Maximum Temperature ("*degree*C*")"))+
  ggtitle("a) Weather data with initial response")+
  theme_classic()+
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        axis.text.y = element_text(size = 25),
        axis.text.x = element_text(size = 25),
        axis.title = element_text(size = 25),
        plot.title = element_text(face= "bold"),
        axis.line = element_line(colour = "black"))

ggsave(file.path(graph.wd,"PrecipTempCor.png"), plot = last_plot(), width=7, height=6, dpi = 300, units="in")

# Without transient community 
## to run this code, I need to import data from models
load(file.path(dataout,"DataModel_CoarseEnv/DataModel_DistMinus5y_CoarseEnv.RData"))

clim.matrix.df <- as_tibble(clim.matrix)

fit <- lm(Precip_mm ~ MaxTemp_C, data=clim.matrix.df)
correlation <- cor(clim.matrix.df$Precip_mm,clim.matrix.df$MaxTemp_C)


ggplot(data = clim.matrix.df, aes(y = Precip_mm, x = MaxTemp_C)) +
  stat_function(fun = function(x) predict(fit, newdata = data.frame(MaxTemp_C = x)),
                color = "black", linewidth = 2) +
  annotate(label = sprintf("y = %.3f + %.3f x\nR² = %.2f", coef(fit)[1], coef(fit)[2], summary(fit)$r.squared),
           geom = "text", x = 0, y = 230, size = 5) +
  annotate(label = paste0("cor = ",round(correlation,2)),
           geom = "text", x = 0, y = 205, size = 5) +
  geom_point(shape=19,size=5,alpha=0.5) +
  # xlim(0,1300)+
  ylab("Monthly Precipitation (mm)")+
  xlab(expression("Monthly Maximum Temperature ("*degree*C*")"))+
  ggtitle("b) Weather data without initial response")+
  theme_classic()+
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        axis.text.y = element_text(size = 25),
        axis.text.x = element_text(size = 25),
        axis.title = element_text(size = 25),
        plot.title = element_text(face= "bold"),
        axis.line = element_line(colour = "black"))

ggsave(file.path(graph.wd,"PrecipTempCor_Minus5y.png"), plot = last_plot(), width=7, height=6, dpi = 300, units="in")
```