---
title: "L2_dataAnalysis_CDCRdata_Nutrient_AllDist_Figures_CoarseEnv"
author: "laís petri"
date: "2025-03-07"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
rm(list = ls())
started <- Sys.time()
```

```{r package and directory, echo=FALSE}
## data wrangling + plots
library(tidyverse) 
library(scales)
library(patchwork)
## color blind discrete colors
library(pals) 
## arrange plots
library(cowplot)
```

Folders
```{r}
workingdir <- getwd()
datain <- file.path(workingdir, "parameters/CoarseEnv")
graph.wd <- file.path(workingdir, "figures/final")
```

Importing datasets: summary stats
```{r}
# live biomass
## All years
# Intact model results
parameters0_NoDist <- read_csv(file.path(datain,"NoDist_CoarseEnv_ParametersValues.csv")) %>% 
    mutate(exp = 1,
           dur = 1) # 1=All years, 2 = Minus5y
glimpse(parameters0_NoDist)

# Disturbed model results
parameters0_Dist <- read_csv(file.path(datain,"Dist_CoarseEnv_ParametersValues.csv")) %>% 
    mutate(exp = 2,
           dur = 1)
glimpse(parameters0_Dist)

## Minus5y
# Intact model results
parameters0_NoDist2 <- read_csv(file.path(datain,"NoDistMinus5y_CoarseEnv_ParametersValues.csv")) %>% 
    mutate(exp = 1,
           dur = 2)
glimpse(parameters0_NoDist2)

# Disturbed model results
parameters0_Dist2 <- read_csv(file.path(datain,"DistMinus5y_CoarseEnv_ParametersValues.csv")) %>% 
    mutate(exp = 2,
           dur = 2)
glimpse(parameters0_Dist2)
```

Importing datasets: predictions of effect vs ntrt quantity
```{r}
# live biomass
## All years
# Preciptation
precip.pred <- read_csv(file.path(workingdir,"parameters/CoarseEnv_Slopes/abg/precipData_allYears_ParametersValues.csv")) %>% 
  mutate(alpha=2,
         dur = 1)
glimpse(precip.pred)

# temperature
temp.pred <- read_csv(file.path(workingdir,"parameters/CoarseEnv_Slopes/abg/tempData_allYears_ParametersValues.csv")) %>% 
  mutate(alpha=3,
         dur = 1)
glimpse(temp.pred)

## Minus5y
# Precipitation
precip.pred2 <- read_csv(file.path(workingdir,"parameters/CoarseEnv_Slopes/abgMinus5y/precipData_Minus5y_ParametersValues.csv")) %>% 
  mutate(alpha=2,
         dur = 2)
glimpse(precip.pred2)

# temperature
temp.pred2 <- read_csv(file.path(workingdir,"parameters/CoarseEnv_Slopes/abgMinus5y/tempData_Minus5y_ParametersValues.csv")) %>% 
  mutate(alpha=3,
         dur = 2)
glimpse(temp.pred2)

```

Importing datasets: climate means
```{r}
# live biomass
## All years
clim.means_NoDist <- read_csv(file.path(workingdir,"data/L1/DataModel_CoarseEnv/climateMeans/clim.means_NoDist_CoarseEnv.csv")) %>% 
    summarise(Precip_mm = sum(Precip_mm),
              MaxTemp_C = mean(MaxTemp_C)) %>%
  mutate(exp = 1,
         dur = 1)

clim.means_Dist <- read_csv(file.path(workingdir,"data/L1/DataModel_CoarseEnv/climateMeans/clim.means_Dist_CoarseEnv.csv")) %>% 
    summarise(Precip_mm = sum(Precip_mm),
              MaxTemp_C = mean(MaxTemp_C)) %>% 
  mutate(exp = 2,
         dur = 1)

## Minus5y
clim.means_NoDist2 <- read_csv(file.path(workingdir,"data/L1/DataModel_CoarseEnv/climateMeans/clim.means_NoDistMinus5y_CoarseEnv.csv")) %>% 
    summarise(Precip_mm = sum(Precip_mm),
              MaxTemp_C = mean(MaxTemp_C)) %>% 
  mutate(exp = 1,
         dur = 2)

clim.means_Dist2 <- read_csv(file.path(workingdir,"data/L1/DataModel_CoarseEnv/climateMeans/clim.means_DistMinus5y_CoarseEnv.csv")) %>% 
    summarise(Precip_mm = sum(Precip_mm),
              MaxTemp_C = mean(MaxTemp_C)) %>% 
  mutate(exp = 2,
         dur = 2)

clim.means <- clim.means_NoDist %>% bind_rows(clim.means_Dist) %>% bind_rows(clim.means_NoDist2) %>% bind_rows(clim.means_Dist2)
```

Importing PNG figures
```{r}
icon_rain <- file.path(datain,"PNG/weather-rain.png")
icon_temp <- file.path(datain,"PNG/temperature-moderate.png")
```

# Results (Figures)

Code to plot the output of both models in same plots

General objects (graphs)
```{r}
#colors
colntrt<-pals::brewer.dark2(9)

#trick to plot 9 before all other treatments
order_levels <- c(9, 1, 2, 3, 4, 5, 6, 7, 8)
ntrtLong_levels <- c("0 + None", "0 + All", "1 + All", "2 + All", "3.4 + All", "5.4 + All", "9.5 + All", "17 + All", "27.2 + All")
ntrtLong_levels2 <- c("0\nNone", "0\nAll", "1\nAll", "2\nAll", "3.4\nAll", "5.4\nAll", "9.5\nAll", "17\nAll", "27.2\nAll")

#variable names
summaryVar <- data.frame(Var_name = c("Precipitation","Maximum_Temperature"),
                         Var_name2 = c("P","T"),
                         Var_name3 = c("Precipitation","Maximum Temperature"),
                         biomass = c(1,1),
                         Var_name5 = c("LiveBiomass","LiveBiomass"),
                         variable = c(1,2))

#theme facet
theme_facet <- theme_classic() + 
    theme(legend.position = "none",
          text = element_text(family = "sans"),
          strip.text.x = element_text(face = "bold", size = 11),
          axis.text.y = element_text(size = 10),
          axis.text.x = element_text(size = 7),
          axis.title.y = element_text(size = 10, face = "bold"),
          strip.text.y = element_text(size=9),
          axis.line = element_blank(),
          strip.background = element_rect(linewidth=0.5),
          plot.margin = margin(t = 5, r = 5, b = 20, l = 5))

theme_facet2 <- theme_classic() + 
    theme(legend.position = "none",
          text = element_text(family = "sans"),
          strip.text.x = element_text(face = "bold", size = 11),
          axis.text.y = element_text(size = 10),
          axis.text.x = element_text(size = 7),
          axis.title.x = element_text(size = 14, face = "bold", margin = margin(t=20)),
          strip.text.y = element_text(size=9),
          axis.line = element_blank(),
          strip.background = element_rect(linewidth=0.5),
          plot.margin = margin(t = 5, r = 5, b = 5, l = 5))

theme_regular <- theme_classic() + 
    theme(legend.position = "none",
          text = element_text(family = "sans"),
          strip.text.x = element_text(face = "bold", size = 11),
          axis.text.y = element_text(size = 10),
          axis.text.x = element_text(size = 7),
          axis.title.x = element_blank(),
          axis.title.y = element_text(size = 10, face = "bold"),
          strip.text.y = element_text(size=9),
          axis.line = element_blank(),
          strip.background = element_rect(linewidth=0.5),
          plot.margin = margin(t = 5, r = 75, b = 5, l = 5))

# resolution_export
res_export <- 300
```

Merging model results
```{r}
parameters_All <- rbind(parameters0_NoDist,parameters0_Dist,parameters0_NoDist2,parameters0_Dist2) %>% mutate(biomass=1)
```

## Main
###- [Main] Effect sizes of env var as a function of continuous ntrt
Creating dataset - live biomass
```{r}
## raw data
ntrt_qtt <- tibble(ntrt = as.factor(c(1:9)),
                       ntrt_qtt = c(0.0,1.0,2.0,3.4,5.4,9.5,17.0,27.2,0))

Alphamodelpar<- parameters_All %>% 
  filter(grepl("^mu_a_ntrt.star",parameter)) %>% 
  mutate(alpha = rep(1:4,times=36),
         ntrt = factor(rep(1:9,times=4, each=4), levels = order_levels),
         ntrtLong = factor(rep(c("0 + All", "1 + All", "2 + All", "3.4 + All", "5.4 + All", "9.5 + All", "17 + All", "27.2 + All", "0 + None"),times=4, each=4), levels = ntrtLong_levels),
         filling=ifelse(`quantiles.2.5.`<0&`quantiles.97.5.`<0|                                                              `quantiles.2.5.`>0&`quantiles.97.5.`>0, "other","white"),
         shape=ifelse(exp==1,21,24),
         cat = ifelse(exp==1&dur==1, 1, ifelse(exp==2&dur==1, 2, ifelse(exp==1&dur==2, 3,4)))) %>%
   filter(!(alpha %in% c(1,4))) %>%  #removing intercept and AR
  left_join(ntrt_qtt) %>% 
  mutate(cat = ifelse(dur==1 & exp==2 & ntrt==4, 5, cat))

## predictions ## NOTE: add biomass column here and in a similar code chunk for litter
predictions <- precip.pred %>% 
  filter(grepl("^mu_exp.pred",parameter)) %>% 
  mutate(exp = rep(1:2, times=28),
         ntrtpred = rep(c(seq(0,26,1),27.2), each=2)) %>% 
  bind_rows(temp.pred %>% 
  filter(grepl("^mu_exp.pred",parameter)) %>% 
  mutate(exp = rep(1:2, times=28),
         ntrtpred = rep(c(seq(0,26,1),27.2), each=2))) %>% 
  bind_rows(precip.pred2 %>% 
  filter(grepl("^mu_exp.pred",parameter)) %>% 
  mutate(exp = rep(1:2, times=28),
         ntrtpred = rep(c(seq(0,26,1),27.2), each=2))) %>% 
  bind_rows(temp.pred2 %>% 
  filter(grepl("^mu_exp.pred",parameter)) %>% 
  mutate(exp = rep(1:2, times=28),
         ntrtpred = rep(c(seq(0,26,1),27.2), each=2))) %>% 
  mutate(cat = ifelse(exp==1&dur==1, 1, ifelse(exp==2&dur==1, 2, ifelse(exp==1&dur==2, 3,4))))
```

Plot: Precipitation - live biomass
```{r}
a<-
  Alphamodelpar %>%
  filter(alpha==2) %>% 
  ggplot(aes(x=ntrt_qtt,y=`statistics.Mean`))+
  geom_hline(yintercept = 0, linetype = "dashed", color = "darkgray")+
  geom_errorbar(aes(ymin=`quantiles.2.5.`, ymax=`quantiles.97.5.`,color=as.factor(cat)),
                width=0.3,
                linewidth=0.4,
             alpha=0.4,
             show.legend = F)+
  geom_point(aes(shape = as.factor(exp),color=as.factor(cat)),
             size=3,
             alpha=0.5) +
  geom_line(data=predictions %>% filter(alpha==2), 
            aes(y=statistics.Mean, x=ntrtpred, colour = as.factor(cat)), 
            linewidth=1,
            show.legend = FALSE) +
  geom_ribbon(data=predictions %>% filter(alpha==2),
              aes(ymin=quantiles.2.5., ymax=quantiles.97.5., x=ntrtpred,fill = as.factor(cat)), alpha=0.2)+
  scale_x_continuous(expand = c(0,0),
                     breaks = c(0.0,1.0,2.0,3.4,5.4,9.5,17.0,27.2))+
  scale_y_continuous(breaks = seq(-5,25, by=5),
                     labels = c("-5.0","0.0","5.0","10.0","15.0","20.0", "25.0"))+
  scale_color_manual(values = c(pals::cols25(5)[4], pals::cols25(5)[5],pals::cols25(5)[4], pals::cols25(5)[5], "gray30"))+
  scale_fill_manual(values = c(pals::cols25(5)[4], pals::cols25(5)[5],pals::cols25(5)[4], pals::cols25(5)[5]))+
  scale_shape_manual(values = c(19, 17),
                     labels = c("Intact","Disturbed")) +
  facet_wrap(~dur, nrow=1, 
             labeller = labeller(dur = c("1" = "All Years", "2" = "No Initial Response")))+
  xlab(expression(bold("Nutrient addition (g N/m"^2*"/yr)")))+
  ylab("Effect of past weather on biomass\n(posterior mean ± 95% CIs)")+
  ggtitle("Precipitation")+
  coord_cartesian(clip = "off",
                   xlim=c(-0.3,27.2))+
  theme_regular + 
  theme(legend.margin=margin(-4,3,2,1),
        legend.position = c(0.15,0.90),
        legend.text = element_text(size=12),
        legend.background = element_blank(),
        legend.title = element_blank(),
        axis.text.y = element_text(size = 12),
        axis.text.x = element_blank(),
        axis.ticks.x=element_blank(),
        axis.title.y = element_text(size = 12, face = "bold"),
        axis.title.x = element_blank(),
        title = element_text(face = "bold", size = 12),
        strip.text = element_text(face = "bold", size = 11),
        plot.margin = margin(t = 5, r = 15, b = 0, l = 5),
        panel.spacing = unit(1, "lines")) +
  guides(shape = guide_legend(override.aes = list(alpha=1,size=4,
                                                  color=c(pals::cols25(5)[4],pals::cols25(5)[5]))),
         color = "none",
         fill = "none") +
  geom_segment(data = filter(Alphamodelpar, dur == 1), 
               aes(x = -0.42, xend = -0.42, y = -5, yend = 20), inherit.aes = FALSE, color="gray20")

final_a <- ggdraw(a) +
  draw_label("a)", x = 0.08, y = 0.902, size = 13, fontface = "bold", hjust = 0, vjust = 1) +
  draw_label("b)", x = 0.545, y = 0.902, size = 13, fontface = "bold", hjust = 0, vjust = 1) +
  # Rain cloud
  draw_image(image = icon_rain, x = -0.45, y = 0.385, scale = 0.060)  # Panel A

 final_a
```

Plot: Temperature - live biomass
```{r}
b<-
  Alphamodelpar %>%
  filter(alpha==3) %>% 
  ggplot(aes(x=ntrt_qtt,y=`statistics.Mean`))+
  geom_hline(yintercept = 0, linetype = "dashed", color = "darkgray")+
  geom_errorbar(aes(ymin=`quantiles.2.5.`, ymax=`quantiles.97.5.`,color=as.factor(cat)),
                width=0.3,
                linewidth=0.4,
             alpha=0.4,
             show.legend = F)+
  geom_point(aes(shape = as.factor(exp),color=as.factor(cat)),
             size=3,
             alpha=0.5) +
  geom_line(data=predictions %>% filter(alpha==3), 
            aes(y=statistics.Mean, x=ntrtpred, colour = as.factor(cat)), 
            linewidth=1,
            show.legend = FALSE) +
  geom_ribbon(data=predictions %>% filter(alpha==3),
              aes(ymin=quantiles.2.5., ymax=quantiles.97.5., x=ntrtpred,fill = as.factor(exp)), alpha=0.2)+
  scale_x_continuous(expand = c(0,0),
                     breaks = c(0,1,2,3.4,5.4,9.5,17,27.2),
                     labels = c("0","1","2","3.4","5.4","9.5","17","27.2"))+
  scale_y_continuous(n.breaks = 7) +
  scale_color_manual(values = c(pals::cols25(5)[4], pals::cols25(5)[5],pals::cols25(5)[4], pals::cols25(5)[5], "gray30"))+
  scale_fill_manual(values = c(pals::cols25(5)[4], pals::cols25(5)[5],pals::cols25(5)[4], pals::cols25(5)[5]))+
  scale_shape_manual(values = c(19, 17),
                     labels = c("Intact","Disturbed")) +
  facet_wrap(~dur, nrow=1, 
             labeller = labeller(dur = c("1" = "All Years", "2" = "No Initial Response")))+
  xlab(expression(bold("Nutrient addition (g N/m"^2*"/yr)")))+
  ylab("Effect of past weather on biomass\n(posterior mean ± 95% CIs)")+
  ggtitle("Temperature")+
  coord_cartesian(clip = "off",
                   xlim=c(-0.3,27.2))+
  theme_regular+ 
  theme(legend.margin=margin(-4,3,2,1),
        legend.position = "none", #c(0.10,0.92),
        legend.text = element_text(size=12),
        legend.background = element_blank(),
        legend.title = element_blank(),
        axis.text.y = element_text(size = 12),
        axis.text.x = element_text(size = 10),
        axis.title.y = element_text(size = 12, face = "bold"),
        axis.title.x = element_text(size = 12),
        title = element_text(face = "bold", size = 12),
        strip.text = element_text(face = "bold", size = 11),
        plot.margin = margin(t = 5, r = 15, b = 0, l = 5),
        panel.spacing = unit(1, "lines")) +
  guides(shape = guide_legend(override.aes = list(alpha=1,size=4,
                                                  color=c(pals::cols25(5)[4],pals::cols25(5)[5]))),
         color = "none",
         fill = "none")+
  geom_segment(data = filter(Alphamodelpar),
               aes(x = 0, xend = 27.2, y = -Inf, yend = -Inf), inherit.aes = FALSE, color="gray20") +
  geom_segment(data = filter(Alphamodelpar, dur == 1), 
               aes(x = -0.42, xend = -0.42, y = -50, yend = 200), inherit.aes = FALSE, color="gray20")

final_b <- ggdraw(b) +
  draw_label("c)", x = 0.08, y = 0.905, size = 13, fontface = "bold", hjust = 0, vjust = 1) +
  draw_label("d)", x = 0.545, y = 0.905, size = 13, fontface = "bold", hjust = 0, vjust = 1) +
  # Rain cloud
  draw_image(image = icon_temp, x = -0.45, y = 0.39, scale = 0.080)  # Panel A.

 final_b
```

Merge plots
```{r}
full <- plot_grid(final_a, final_b, nrow=2, ncol = 1, rel_heights = c(0.95,1))
full

ggsave(file.path(graph.wd,"Fig2_EnvCoefVSNtrt.png"), plot = last_plot(), width=11, height=8, dpi = res_export, units="in")
```

###- [Main] Memory Temporal Patterns
Creating datasets
```{r}
# live biomass
#dataframe
WEIGHTMomodelpar <- parameters_All %>% 
  filter(grepl("^weightOrdered",parameter)) %>% 
  mutate(ntrt = factor(rep(1:9,times=288, each=1), levels = order_levels),
         ntrtLong = factor(rep(c("0 + All", "1 + All", "2 + All", "3.4 + All", "5.4 + All", "9.5 + All", "17 + All", "27.2 + All", "0 + None"),times=288, each=1), levels = ntrtLong_levels),
         month = rep(1:36,times=8, each=9),
         variable = rep(1:2,times=4, each=324),
         ntrt=factor(ntrt, levels = order_levels)) 

WEIGHTMomodelpar1 <- WEIGHTMomodelpar %>% 
  filter(month %in% seq(2,36, by=3))
```

Plots
```{r}
a<-
  WEIGHTMomodelpar %>% 
  filter(variable==1, #dur==2, 
         ) %>% # precip, all data, intact
  ggplot(aes(x=month,y=`statistics.Mean`,
             color=as.factor(exp))) +
  annotate("rect", xmin = 3.5, xmax = 9.5, ymin = -Inf, ymax = Inf, alpha = .05) +
    annotate("rect", xmin = 15.5, xmax = 21.5, ymin = -Inf, ymax = Inf, alpha = .05) +
    annotate("rect", xmin = 27.5, xmax = 33.5, ymin = -Inf, ymax = Inf, alpha = .05) +
    geom_vline(xintercept = seq(3.5, 36, by = 3), color = "gray", linetype = "dashed") +
    geom_vline(xintercept = seq(12.5, 36, by = 12), color = "gray50") +
  geom_line(aes(linetype = as.factor(dur)), linewidth=1) +
  scale_color_manual(values = c(pals::cols25(5)[4], pals::cols25(5)[5]),
                     labels = c("1" = "Intact", "2" = "Disturbed")
                     # guide = "none"
                     ) +  
  scale_linetype_manual(values = c("1" = "solid", "2" = "dotted"),
                        labels = c("1" = "All years", "2" = "No initial\nresponse")) +
 scale_x_continuous(expand = c(0.01,0),
                       breaks = seq(2,36, by=3),
                       labels = rep(c("D-O\nfall","S-J\nlate\nGS","J-A\nearly\nGS","M-J\nwinter"), times=3))+
  facet_wrap(~ntrtLong) +
  xlab("Months in the past") +
  ylab("Relative importance of\npast weather on live biomass")+
  coord_cartesian(ylim = c(0,0.15), 
                    xlim=c(0,36), 
                  clip = "off")+
  geom_segment(data = filter(WEIGHTMomodelpar, ntrt %in% c(9,3,6)),
               aes(x = -0.72, xend = -0.72, y = 0, yend = 0.15), inherit.aes = FALSE, color="gray20") +
  geom_segment(data = filter(WEIGHTMomodelpar, ntrt %in% c(6,7,8)),  #WEIGHTMomodelpar,
               aes(x = 0, xend = 36, y = -Inf, yend = -Inf), inherit.aes = FALSE, color="gray20")+
    annotate("text", x = 6.5, y = -0.58, label = "y0", color = "gray30", fontface = "bold", size = 3.5) +
    annotate("text", x = 18.5, y = -0.58, label = "y-1", color = "gray30", fontface = "bold", size = 3.5) + 
    annotate("text", x = 30.5, y = -0.58, label = "y-2", color = "gray30", fontface = "bold", size = 3.5) +
  geom_text(data = filter(WEIGHTMomodelpar, ntrt %in% c(9)),  #WEIGHTMomodelpar,
               aes(x = 9.5, y = 0.225), inherit.aes = FALSE, label = "a) Precipitation", color = "black", size = 5, fontface = "bold")+
  theme_facet2+
  theme(legend.position = "top",
        legend.title = element_blank(),
        legend.justification = "right",
        legend.spacing = unit(0, "cm"),
        legend.margin = margin(t = 0, r = 0, b = 0, l = 0, unit = "cm"),
        legend.text = element_text(margin = margin(r = 5)),
        legend.box.spacing = unit(0, "cm"),  # Reduces space between legend and plot
        legend.box.margin = margin(t=0, r=0, b=1, l=0), # Removes internal legend box margin
        legend.spacing.y = unit(0, "cm"),  # Adjusts vertical space between legend keys
        plot.margin = margin(t = 5, r = 5, b = 5, l = 10),
        axis.title.y = element_text(size = 12, face = "bold"),
        axis.title.x = element_blank(),
        axis.text.x = element_blank())

final_a <- ggdraw(a) +
  # Rain cloud
  draw_image(image = icon_rain, x = -0.460, y =  0.445, scale = 0.05)
final_a

# temperature
b<-
  WEIGHTMomodelpar %>% 
  filter(variable==2, #dur==2, 
         ) %>% # precip, all data, intact
  ggplot(aes(x=month,y=`statistics.Mean`,
             color=as.factor(exp))) +
  annotate("rect", xmin = 3.5, xmax = 9.5, ymin = -Inf, ymax = Inf, alpha = .05) +
    annotate("rect", xmin = 15.5, xmax = 21.5, ymin = -Inf, ymax = Inf, alpha = .05) +
    annotate("rect", xmin = 27.5, xmax = 33.5, ymin = -Inf, ymax = Inf, alpha = .05) +
    geom_vline(xintercept = seq(3.5, 36, by = 3), color = "gray", linetype = "dashed") +
    geom_vline(xintercept = seq(12.5, 36, by = 12), color = "gray50") +
  geom_line(aes(linetype = as.factor(dur)), linewidth=1) +
  scale_color_manual(values = c(pals::cols25(5)[4], pals::cols25(5)[5]),
                     labels = c("1" = "Intact", "2" = "Disturbed")
                     # guide = "none"
                     ) +  
  scale_linetype_manual(values = c("1" = "solid", "2" = "dotted"),
                        labels = c("1" = "All years", "2" = "No initial\nresponse")) +
  scale_x_continuous(expand = c(0.01,0),
                       breaks = seq(2,36, by=3),
                       labels = rep(c("D-O\nfall","S-J\nlate\nGS","J-A\nearly\nGS","M-J\nwinter"), times=3))+
  facet_wrap(~ntrtLong) +
  xlab("Months in the past") +
  ylab("Relative importance of\npast weather on live biomass")+
  coord_cartesian(ylim = c(0,0.15), 
                    xlim=c(0,36), 
                  clip = "off")+
  geom_segment(data = filter(WEIGHTMomodelpar, ntrt %in% c(9,3,6)),
               aes(x = -0.72, xend = -0.72, y = 0, yend = 0.15), inherit.aes = FALSE, color="gray20") +
  geom_segment(data = filter(WEIGHTMomodelpar, ntrt %in% c(6,7,8)),  #WEIGHTMomodelpar,
               aes(x = 0, xend = 36, y = -Inf, yend = -Inf), inherit.aes = FALSE, color="gray20")+
    annotate("text", x = 6.5, y = -0.56, label = "y0", color = "gray30", fontface = "bold", size = 3.5) +
    annotate("text", x = 18.5, y = -0.56, label = "y-1", color = "gray30", fontface = "bold", size = 3.5) + 
    annotate("text", x = 30.5, y = -0.56, label = "y-2", color = "gray30", fontface = "bold", size = 3.5) +
  geom_text(data = filter(WEIGHTMomodelpar, ntrt %in% c(9)),  #WEIGHTMomodelpar,
               aes(x = 9.5, y = 0.240), inherit.aes = FALSE, label = "b) Temperature", color = "black", size = 5, fontface = "bold")+
  theme_facet2+
  theme(legend.position = "none",
        legend.title = element_blank(),
        legend.justification = "right",
        legend.spacing = unit(0, "cm"),
        legend.margin = margin(t = 0, r = 0, b = 0, l = 0, unit = "cm"),
        legend.text = element_text(margin = margin(r = 5)),
        legend.box.spacing = unit(0, "cm"),  # Reduces space between legend and plot
        legend.box.margin = margin(t=0, r=0, b=1, l=0), # Removes internal legend box margin
        legend.spacing.y = unit(0, "cm"),  # Adjusts vertical space between legend keys
        axis.title.y = element_text(size = 12, face = "bold"),
        plot.margin = margin(t = 25, r = 5, b = 5, l = 10))

final_b <- ggdraw(b) +
  # Rain cloud
  draw_image(image = icon_temp, x = -0.460, y =  0.450, scale = 0.06)
final_b

# Merge plots

left_column <- plot_grid(final_a, final_b, ncol = 1, rel_heights = c(0.87,1))
left_column

ggsave(file.path(graph.wd,"Fig3_MemoryTempPattern_LiveBiomass.png"), plot = last_plot(), width=11, height=9, dpi = res_export, units="in")
```

###- [Main] Memory length (cumulative weight)
Creating dataset - live biomass
50%
```{r}
ntrt_database <- tibble(ntrt = factor(1:9, levels = order_levels),
         ntrtLong = factor(c("0\nAll", "1\nAll", "2\nAll", "3.4\nAll", "5.4\nAll", "9.5\nAll", "17\nAll", "27.2\nAll", "0\nNone"), levels = ntrtLong_levels2)) 

# Create a sequence of thresholds
thresholds <- seq(0.5, 1, by = 0.01)

# Initialize the dataframe
WEIGHTMoLength <- WEIGHTMomodelpar %>%
  group_by(exp, ntrt, variable, dur) %>%
  arrange(exp, ntrt, variable, month) %>%
  mutate(cumulative_sum = cumsum(statistics.Mean)) 

# Loop over each threshold and calculate the months_no
for (threshold in thresholds) {
  WEIGHTMoLength <- WEIGHTMoLength %>%
    mutate(!!sym(paste0("months_no_", threshold)) := min(month[cumulative_sum >= threshold], na.rm = TRUE))
}

# Summarise to get the final result
WEIGHTMoLength <- WEIGHTMoLength %>%
  summarise(across(starts_with("months_no_"), ~ min(.x, na.rm = TRUE), .names = "min_{.col}"), .groups = "drop") %>%
  ungroup() %>%
  group_by(dur, exp, ntrt, variable) %>% 
  pivot_longer(cols = starts_with("min_months_no_"),
               names_to = "length",
               values_to = "months_no") %>% 
  mutate(months_no = ifelse(months_no==Inf, 36, months_no)) %>% 
  # Pivot wider to have separate columns for exp == 1 and exp == 2
  pivot_wider(names_from = exp, 
              values_from = "months_no", 
              names_prefix = "exp_") %>% 
  # Calculate mem_length
  mutate(mem_length = exp_1 - exp_2) %>% 
  left_join(ntrt_database)

WEIGHTMoLength <- WEIGHTMoLength %>% 
  group_by(ntrt, variable, dur, ntrtLong) %>% 
  summarise(mean_mem_length = mean(mem_length), sd_mem_length = sd(mem_length)) %>% 
  mutate(color_group = ifelse(mean_mem_length >= 0, "positive", "negative"),
         color_group = ifelse(dur==1 & ntrt==4, 'neutral', color_group))
```

Plot side-by-side: Precipitation - live biomass
```{r}
a<-
  WEIGHTMoLength %>%
  filter(variable==1) %>% 
  ggplot(aes(y=mean_mem_length,
             x=ntrtLong,
             fill=color_group))+
  geom_boxplot(alpha = 0.3, outlier.size = 0, size=0.3) + 
  geom_bar(stat = "identity", color = NA, size = 0) +
  geom_errorbar(aes(
    ymin = mean_mem_length - sd_mem_length,
    ymax = mean_mem_length + sd_mem_length,
    color = color_group
  ), width = 0.3, size = 0.3)+
    geom_hline(yintercept = 0, linetype = "dashed", color = "black") +
  scale_fill_manual(values = c("positive" = "#6A33C2",  # purple
                             "negative" = "#ff7f00",
                             "neutral" = "gray70")) + # orange
  scale_color_manual(values = c("positive" = "#6A33C2",  # purple
                             "negative" = "#ff7f00",
                             "neutral" = "gray70")) + # orange
  scale_shape_manual(values =c(21,24))+
  scale_y_continuous(breaks = c(6,3,0,-3,-6),
                     labels = function(y) format(y, nsmall = 1, digits = 1)) +
  coord_cartesian(ylim = c(-6,6), 
                  xlim = c(1,9),
                  clip = "off")+
  facet_grid(~dur, labeller = labeller(dur = c("1" = "All Years", "2" = "No Initial Response"))) +
  ylab("Difference in months when\nmemory length is >50%\n(mean ± sd)")+
  xlab("")+  
  ggtitle("Precipitation")+
  geom_segment(data = filter(WEIGHTMoLength, dur == 1),
               aes(x = 0.27, xend = 0.27, y = -6, yend = 6), inherit.aes = FALSE, color="gray20") +
  annotate("segment", y=-Inf, yend=-Inf, x=1, xend=9, color = "gray20") +
  annotate("segment", y=.5, yend=6, x=10, xend=10, color = "gray20") +
  annotate("segment", y=-.5, yend=-6, x=10, xend=10, color = "gray20") +
  geom_segment(data = filter(WEIGHTMoLength, dur == 2), 
               aes(x = 9.7, xend = 10, y = 6, yend = 6), inherit.aes = FALSE, color="gray20", linewidth=0.3)+
  geom_segment(data = filter(WEIGHTMoLength, dur == 2), 
               aes(x = 9.7, xend = 10, y = 0.5, yend = 0.5), inherit.aes = FALSE, color="gray20", linewidth=0.3)+
  geom_segment(data = filter(WEIGHTMoLength, dur == 2), 
               aes(x = 9.7, xend = 10, y = -0.5, yend = -0.5), inherit.aes = FALSE, color="gray20", linewidth=0.3)+
  geom_segment(data = filter(WEIGHTMoLength, dur == 2), 
               aes(x = 9.7, xend = 10, y = -6, yend = -6), inherit.aes = FALSE, color="gray20", linewidth=0.3)+
  annotate("text", x = 11.75, y = 6.55, label = "Longer\nMemory\nin:", color = "black", fontface = "bold", size = 3.5)+
  annotate("text", x = 11.75, y = 3.5, label = "\nINTACT\nplots", color = "gray30", fontface = "bold", size = 3.3)+
  annotate("text", x = 11.75, y = -3.5, label = "\nDISTURBED\nplots", color = "gray30", fontface = "bold", size = 3.3)+
  theme_regular +
  theme(plot.margin = margin(t = 2, r = 75, b = 5, l = 5),
        title = element_text(face = "bold", size = 12))

 final_a <- ggdraw(a) +
   draw_label("a)", x = 0.14, y = 0.916, size = 13, fontface = "bold", hjust = 0, vjust = 1)+
   draw_label("b)", x = 0.51, y = 0.916, size = 13, fontface = "bold", hjust = 0, vjust = 1)+
  # Rain cloud
  draw_image(image = icon_rain, x = -0.43, y = 0.4, scale = 0.060)  # Panel A

 final_a
```

Plot side-by-side: Temperature - live biomass
```{r}
b<-
  WEIGHTMoLength %>%
  filter(variable==2) %>% 
ggplot(aes(y=mean_mem_length,
             x=ntrtLong,
             fill=color_group))+
  geom_boxplot(alpha = 0.3, outlier.size = 0, size=0.3) + 
  geom_bar(stat = "identity", color = NA, size = 0) +
  geom_errorbar(aes(
    ymin = mean_mem_length - sd_mem_length,
    ymax = mean_mem_length + sd_mem_length,
     color = color_group
  ), width = 0.3, size = 0.3)+
    geom_hline(yintercept = 0, linetype = "dashed", color = "black") +
  scale_fill_manual(values = c("positive" = "#6A33C2",  # purple
                             "negative" = "#ff7f00",
                             "neutral" = "gray70")) + # orange
  scale_color_manual(values = c("positive" = "#6A33C2",  # purple
                             "negative" = "#ff7f00",
                             "neutral" = "gray70")) + # orange
  scale_shape_manual(values =c(21,24))+
  scale_y_continuous(breaks = c(6,3,0,-4,-8),
                     labels = function(y) format(y, nsmall = 1, digits = 1)) +
  coord_cartesian(ylim = c(-8,6), 
                  xlim = c(1,9),
                  clip = "off")+
  facet_grid(~dur, labeller = labeller(dur = c("1" = "All Years", "2" = "No Initial Response"))) +
  ylab("Difference in months when\nmemory length is >50%\n(mean ± sd)")+
  xlab("")+  
  ggtitle("Temperature")+
  geom_segment(data = filter(WEIGHTMoLength, dur == 1), 
               aes(x = 0.27, xend = 0.27, y = -8, yend = 6), inherit.aes = FALSE, color="gray20") +
  annotate("segment", y=-Inf, yend=-Inf, x=1, xend=9, color = "gray20") +
  annotate("segment", y=.5, yend=6, x=10, xend=10, color = "gray20") +
  annotate("segment", y=-.5, yend=-8, x=10, xend=10, color = "gray20") +
  geom_segment(data = filter(WEIGHTMoLength, dur == 2), 
               aes(x = 9.7, xend = 10, y = 6, yend = 6), inherit.aes = FALSE, color="gray20", linewidth=0.3)+
  geom_segment(data = filter(WEIGHTMoLength, dur == 2), 
               aes(x = 9.7, xend = 10, y = 0.5, yend = 0.5), inherit.aes = FALSE, color="gray20", linewidth=0.3)+
  geom_segment(data = filter(WEIGHTMoLength, dur == 2), 
               aes(x = 9.7, xend = 10, y = -0.5, yend = -0.5), inherit.aes = FALSE, color="gray20", linewidth=0.3)+
  geom_segment(data = filter(WEIGHTMoLength, dur == 2), 
               aes(x = 9.7, xend = 10, y = -8, yend = -8), inherit.aes = FALSE, color="gray20", linewidth=0.3)+
  annotate("text", x = 11.75, y = 6.75, label = "Longer\nMemory\nin:", color = "black", fontface = "bold", size = 3.5)+
  annotate("text", x = 11.75, y = 3.5, label = "\nINTACT\nplots", color = "gray30", fontface = "bold", size = 3.3)+
  annotate("text", x = 11.75, y = -4.5, label = "\nDISTURBED\nplots", color = "gray30", fontface = "bold", size = 3.3)+
  theme_regular +
  theme(plot.margin = margin(t = 2, r = 75, b = 5, l = 5),
        title = element_text(face = "bold", size = 12))

 final_b <- ggdraw(b) +
   draw_label("c)", x = 0.14, y = 0.916, size = 13, fontface = "bold", hjust = 0, vjust = 1)+
   draw_label("d)", x = 0.51, y = 0.916, size = 13, fontface = "bold", hjust = 0, vjust = 1) +
  # Rain cloud
  draw_image(image = icon_temp, x = -0.43, y = 0.4, scale = 0.080)   # Panel A

 final_b
```

Merge side-by-side plots - live biomass
```{r}
left_column <- plot_grid(final_a, final_b, ncol = 1)
left_column
ggsave(file.path(graph.wd,"Fig4_DiffMemoryLength_LiveBiomass.png"), plot = last_plot(), width=7, height=8, dpi = res_export, units="in")
```

75%
```{r}
ntrt_database <- tibble(ntrt = factor(1:9, levels = order_levels),
         ntrtLong = factor(c("0\nAll", "1\nAll", "2\nAll", "3.4\nAll", "5.4\nAll", "9.5\nAll", "17\nAll", "27.2\nAll", "0\nNone"), levels = ntrtLong_levels2)) 

# Create a sequence of thresholds
thresholds <- seq(0.75, 1, by = 0.01)

# Initialize the dataframe
WEIGHTMoLength <- WEIGHTMomodelpar %>%
  group_by(exp, ntrt, variable, dur) %>%
  arrange(exp, ntrt, variable, month) %>%
  mutate(cumulative_sum = cumsum(statistics.Mean)) 

# Loop over each threshold and calculate the months_no
for (threshold in thresholds) {
  WEIGHTMoLength <- WEIGHTMoLength %>%
    mutate(!!sym(paste0("months_no_", threshold)) := min(month[cumulative_sum >= threshold], na.rm = TRUE))
}

# Summarise to get the final result
WEIGHTMoLength <- WEIGHTMoLength %>%
  summarise(across(starts_with("months_no_"), ~ min(.x, na.rm = TRUE), .names = "min_{.col}"), .groups = "drop") %>%
  ungroup() %>%
  group_by(dur, exp, ntrt, variable) %>% 
  pivot_longer(cols = starts_with("min_months_no_"),
               names_to = "length",
               values_to = "months_no") %>% 
  mutate(months_no = ifelse(months_no==Inf, 36, months_no)) %>% 
  # Pivot wider to have separate columns for exp == 1 and exp == 2
  pivot_wider(names_from = exp, 
              values_from = "months_no", 
              names_prefix = "exp_") %>% 
  # Calculate mem_length
  mutate(mem_length = exp_1 - exp_2) %>% 
  left_join(ntrt_database)

WEIGHTMoLength <- WEIGHTMoLength %>% 
  group_by(ntrt, variable, dur, ntrtLong) %>% 
  summarise(mean_mem_length = mean(mem_length), sd_mem_length = sd(mem_length)) %>% 
  mutate(color_group = ifelse(mean_mem_length >= 0, "positive", "negative"))
```

Plot side-by-side: Precipitation - live biomass
```{r}
a<-
  WEIGHTMoLength %>%
  filter(variable==1) %>% 
  ggplot(aes(y=mean_mem_length,
             x=ntrtLong,
             fill=color_group))+
  geom_boxplot(alpha = 0.3, outlier.size = 0, size=0.3) + 
  geom_bar(stat = "identity", color = "black", size = 0) +
  geom_errorbar(aes(
    ymin = mean_mem_length - sd_mem_length,
    ymax = mean_mem_length + sd_mem_length,
    color = color_group
  ), width = 0.3, size = 0.3)+
    geom_hline(yintercept = 0, linetype = "dashed", color = "black") +
  scale_fill_manual(values = c("positive" = "#6A33C2",  # purple
                             "negative" = "#ff7f00")) + # orange
  scale_color_manual(values = c("positive" = "#6A33C2",  # purple
                             "negative" = "#ff7f00")) + # orange
  scale_shape_manual(values =c(21,24))+
  scale_y_continuous(breaks = c(6,3,0,-3,-6),
                     labels = function(y) format(y, nsmall = 1, digits = 1)) +
  coord_cartesian(ylim = c(-6,6), 
                  xlim = c(1,9),
                  clip = "off")+
  facet_grid(~dur, labeller = labeller(dur = c("1" = "All Years", "2" = "No Initial Response"))) +
  ylab("Difference in months when\nmemory length is >75%\n(mean ± sd)")+
  xlab("")+  
  geom_segment(data = filter(WEIGHTMoLength, dur == 1),
               aes(x = 0.27, xend = 0.27, y = -6, yend = 6), inherit.aes = FALSE, color="gray20") +
  annotate("segment", y=-Inf, yend=-Inf, x=1, xend=9, color = "gray20") +
  annotate("segment", y=.5, yend=6, x=10, xend=10, color = "gray20") +
  annotate("segment", y=-.5, yend=-6, x=10, xend=10, color = "gray20") +
  geom_segment(data = filter(WEIGHTMoLength, dur == 2), 
               aes(x = 9.7, xend = 10, y = 6, yend = 6), inherit.aes = FALSE, color="gray20", linewidth=0.3)+
  geom_segment(data = filter(WEIGHTMoLength, dur == 2), 
               aes(x = 9.7, xend = 10, y = 0.5, yend = 0.5), inherit.aes = FALSE, color="gray20", linewidth=0.3)+
  geom_segment(data = filter(WEIGHTMoLength, dur == 2), 
               aes(x = 9.7, xend = 10, y = -0.5, yend = -0.5), inherit.aes = FALSE, color="gray20", linewidth=0.3)+
  geom_segment(data = filter(WEIGHTMoLength, dur == 2), 
               aes(x = 9.7, xend = 10, y = -6, yend = -6), inherit.aes = FALSE, color="gray20", linewidth=0.3)+
  annotate("text", x = 11.75, y = 6.55, label = "Longer\nMemory\nin:", color = "black", fontface = "bold", size = 3.5)+
  annotate("text", x = 11.75, y = 3.5, label = "\nINTACT\nplots", color = "gray30", fontface = "bold", size = 3.3)+
  annotate("text", x = 11.75, y = -3.5, label = "\nDISTURBED\nplots", color = "gray30", fontface = "bold", size = 3.3)+
  geom_text(data = filter(WEIGHTMoLength, dur == 1),
               aes(x = 2.5, y = 8.2), inherit.aes = FALSE, label = "Precipitation", color = "black", size = 5, fontface = "bold")+
  theme_regular +
  theme(plot.margin = margin(t = 15, r = 75, b = 5, l = 5))

 final_a <- ggdraw(a) +
   draw_label("a)", x = 0.14, y = 0.939, size = 13, fontface = "bold", hjust = 0, vjust = 1)+
   draw_label("b)", x = 0.51, y = 0.939, size = 13, fontface = "bold", hjust = 0, vjust = 1)+
  # Rain cloud
  draw_image(image = icon_rain, x = -0.43, y = 0.45, scale = 0.050) +  # Panel A
  draw_label("†", x = 0.300, y = 0.405, size = 10, fontface = "bold", hjust = 0, vjust = 1, color = "#ffba76")
 
 final_a
```

Plot side-by-side: Temperature - live biomass
```{r}
b<-
  WEIGHTMoLength %>%
  filter(variable==2) %>% 
ggplot(aes(y=mean_mem_length,
             x=ntrtLong,
             fill=color_group))+
  geom_boxplot(alpha = 0.3, outlier.size = 0, size=0.3) + 
  geom_bar(stat = "identity", color = NA, size = 0) +
  geom_errorbar(aes(
    ymin = mean_mem_length - sd_mem_length,
    ymax = mean_mem_length + sd_mem_length,
     color = color_group
  ), width = 0.3, size = 0.3)+
    geom_hline(yintercept = 0, linetype = "dashed", color = "black") +
  scale_fill_manual(values = c("positive" = "#6A33C2",  # purple
                             "negative" = "#ff7f00")) + # orange
  scale_color_manual(values = c("positive" = "#6A33C2",  # purple
                             "negative" = "#ff7f00")) + # orange
  scale_shape_manual(values =c(21,24))+
  scale_y_continuous(breaks = c(6,3,0,-4,-8),
                     labels = function(y) format(y, nsmall = 1, digits = 1)) +
  coord_cartesian(ylim = c(-8,6), 
                  xlim = c(1,9),
                  clip = "off")+
  facet_grid(~dur, labeller = labeller(dur = c("1" = "All Years", "2" = "No Initial Response"))) +
  ylab("Difference in months when\nmemory length is >75%\n(mean ± sd)")+
  xlab("")+  
  geom_segment(data = filter(WEIGHTMoLength, dur == 1), 
               aes(x = 0.27, xend = 0.27, y = -8, yend = 6), inherit.aes = FALSE, color="gray20") +
  annotate("segment", y=-Inf, yend=-Inf, x=1, xend=9, color = "gray20") +
  annotate("segment", y=.5, yend=6, x=10, xend=10, color = "gray20") +
  annotate("segment", y=-.5, yend=-8, x=10, xend=10, color = "gray20") +
  geom_segment(data = filter(WEIGHTMoLength, dur == 2), 
               aes(x = 9.7, xend = 10, y = 6, yend = 6), inherit.aes = FALSE, color="gray20", linewidth=0.3)+
  geom_segment(data = filter(WEIGHTMoLength, dur == 2), 
               aes(x = 9.7, xend = 10, y = 0.5, yend = 0.5), inherit.aes = FALSE, color="gray20", linewidth=0.3)+
  geom_segment(data = filter(WEIGHTMoLength, dur == 2), 
               aes(x = 9.7, xend = 10, y = -0.5, yend = -0.5), inherit.aes = FALSE, color="gray20", linewidth=0.3)+
  geom_segment(data = filter(WEIGHTMoLength, dur == 2), 
               aes(x = 9.7, xend = 10, y = -8, yend = -8), inherit.aes = FALSE, color="gray20", linewidth=0.3)+
  annotate("text", x = 11.75, y = 6.75, label = "Longer\nMemory\nin:", color = "black", fontface = "bold", size = 3.5)+
  annotate("text", x = 11.75, y = 3.5, label = "\nINTACT\nplots", color = "gray30", fontface = "bold", size = 3.3)+
  annotate("text", x = 11.75, y = -4.5, label = "\nDISTURBED\nplots", color = "gray30", fontface = "bold", size = 3.3)+
  geom_text(data = filter(WEIGHTMoLength, dur == 1),
               aes(x = 2.5, y = 8.5), inherit.aes = FALSE, label = "Temperature", color = "black", size = 5, fontface = "bold")+
  theme_regular +
  theme(plot.margin = margin(t = 15, r = 75, b = 5, l = 5))

 final_b <- ggdraw(b) +
   draw_label("c)", x = 0.14, y = 0.939, size = 13, fontface = "bold", hjust = 0, vjust = 1)+
   draw_label("d)", x = 0.51, y = 0.939, size = 13, fontface = "bold", hjust = 0, vjust = 1) +
  # Rain cloud
  draw_image(image = icon_temp, x = -0.43, y = 0.45, scale = 0.080) +  # Panel A
  draw_label("†", x = 0.300, y = 0.420, size = 10, fontface = "bold", hjust = 0, vjust = 1, color = "#ffba76")
 
 final_b
```

Merge side-by-side plots - live biomass
```{r}
left_column <- plot_grid(final_a, final_b, ncol = 1)
left_column
ggsave(file.path(graph.wd,"EXTRA_Fig4_DiffMemoryLength_75_LiveBiomass.png"), plot = last_plot(), width=7, height=8, dpi = res_export, units="in")
```

90%
```{r}
ntrt_database <- tibble(ntrt = factor(1:9, levels = order_levels),
         ntrtLong = factor(c("0\nAll", "1\nAll", "2\nAll", "3.4\nAll", "5.4\nAll", "9.5\nAll", "17\nAll", "27.2\nAll", "0\nNone"), levels = ntrtLong_levels2)) 

# Create a sequence of thresholds
thresholds <- seq(0.9, 1, by = 0.01)

# Initialize the dataframe
WEIGHTMoLength <- WEIGHTMomodelpar %>%
  group_by(exp, ntrt, variable, dur) %>%
  arrange(exp, ntrt, variable, month) %>%
  mutate(cumulative_sum = cumsum(statistics.Mean)) 

# Loop over each threshold and calculate the months_no
for (threshold in thresholds) {
  WEIGHTMoLength <- WEIGHTMoLength %>%
    mutate(!!sym(paste0("months_no_", threshold)) := min(month[cumulative_sum >= threshold], na.rm = TRUE))
}

# Summarise to get the final result
WEIGHTMoLength <- WEIGHTMoLength %>%
  summarise(across(starts_with("months_no_"), ~ min(.x, na.rm = TRUE), .names = "min_{.col}"), .groups = "drop") %>%
  ungroup() %>%
  group_by(dur, exp, ntrt, variable) %>% 
  pivot_longer(cols = starts_with("min_months_no_"),
               names_to = "length",
               values_to = "months_no") %>% 
  mutate(months_no = ifelse(months_no==Inf, 36, months_no)) %>% 
  # Pivot wider to have separate columns for exp == 1 and exp == 2
  pivot_wider(names_from = exp, 
              values_from = "months_no", 
              names_prefix = "exp_") %>% 
  # Calculate mem_length
  mutate(mem_length = exp_1 - exp_2) %>% 
  left_join(ntrt_database)

WEIGHTMoLength <- WEIGHTMoLength %>% 
  group_by(ntrt, variable, dur, ntrtLong) %>% 
  summarise(mean_mem_length = mean(mem_length), sd_mem_length = sd(mem_length)) %>% 
  mutate(color_group = ifelse(mean_mem_length >= 0, "positive", "negative"))
```

Plot side-by-side: Precipitation - live biomass
```{r}
a<-
  WEIGHTMoLength %>%
  filter(variable==1) %>% 
  ggplot(aes(y=mean_mem_length,
             x=ntrtLong,
             fill=color_group))+
  geom_boxplot(alpha = 0.3, outlier.size = 0, size=0.3) + 
  geom_bar(stat = "identity", color = "black", size = 0) +
  geom_errorbar(aes(
    ymin = mean_mem_length - sd_mem_length,
    ymax = mean_mem_length + sd_mem_length,
    color = color_group
  ), width = 0.3, size = 0.3)+
    geom_hline(yintercept = 0, linetype = "dashed", color = "black") +
  scale_fill_manual(values = c("positive" = "#6A33C2",  # purple
                             "negative" = "#ff7f00")) + # orange
  scale_color_manual(values = c("positive" = "#6A33C2",  # purple
                             "negative" = "#ff7f00")) + # orange
  scale_shape_manual(values =c(21,24))+
  scale_y_continuous(breaks = c(6,3,0,-3,-6),
                     labels = function(y) format(y, nsmall = 1, digits = 1)) +
  coord_cartesian(ylim = c(-6,6), 
                  xlim = c(1,9),
                  clip = "off")+
  facet_grid(~dur, labeller = labeller(dur = c("1" = "All Years", "2" = "No Initial Response"))) +
  ylab("Difference in months when\nmemory length is >90%\n(mean ± sd)")+
  xlab("")+  
  geom_segment(data = filter(WEIGHTMoLength, dur == 1),
               aes(x = 0.27, xend = 0.27, y = -6, yend = 6), inherit.aes = FALSE, color="gray20") +
  annotate("segment", y=-Inf, yend=-Inf, x=1, xend=9, color = "gray20") +
  annotate("segment", y=.5, yend=6, x=10, xend=10, color = "gray20") +
  annotate("segment", y=-.5, yend=-6, x=10, xend=10, color = "gray20") +
  geom_segment(data = filter(WEIGHTMoLength, dur == 2), 
               aes(x = 9.7, xend = 10, y = 6, yend = 6), inherit.aes = FALSE, color="gray20", linewidth=0.3)+
  geom_segment(data = filter(WEIGHTMoLength, dur == 2), 
               aes(x = 9.7, xend = 10, y = 0.5, yend = 0.5), inherit.aes = FALSE, color="gray20", linewidth=0.3)+
  geom_segment(data = filter(WEIGHTMoLength, dur == 2), 
               aes(x = 9.7, xend = 10, y = -0.5, yend = -0.5), inherit.aes = FALSE, color="gray20", linewidth=0.3)+
  geom_segment(data = filter(WEIGHTMoLength, dur == 2), 
               aes(x = 9.7, xend = 10, y = -6, yend = -6), inherit.aes = FALSE, color="gray20", linewidth=0.3)+
  annotate("text", x = 11.75, y = 6.55, label = "Longer\nMemory\nin:", color = "black", fontface = "bold", size = 3.5)+
  annotate("text", x = 11.75, y = 3.5, label = "\nINTACT\nplots", color = "gray30", fontface = "bold", size = 3.3)+
  annotate("text", x = 11.75, y = -3.5, label = "\nDISTURBED\nplots", color = "gray30", fontface = "bold", size = 3.3)+
  geom_text(data = filter(WEIGHTMoLength, dur == 1),
               aes(x = 2.5, y = 8.2), inherit.aes = FALSE, label = "Precipitation", color = "black", size = 5, fontface = "bold")+
  theme_regular +
  theme(plot.margin = margin(t = 15, r = 75, b = 5, l = 5))

 final_a <- ggdraw(a) +
   draw_label("a)", x = 0.14, y = 0.939, size = 13, fontface = "bold", hjust = 0, vjust = 1)+
   draw_label("b)", x = 0.51, y = 0.939, size = 13, fontface = "bold", hjust = 0, vjust = 1)+
  # Rain cloud
  draw_image(image = icon_rain, x = -0.43, y = 0.45, scale = 0.050) +  # Panel A
  draw_label("†", x = 0.300, y = 0.400, size = 10, fontface = "bold", hjust = 0, vjust = 1, color = "#ffba76")
 
 final_a
```

Plot side-by-side: Temperature - live biomass
```{r}
b<-
  WEIGHTMoLength %>%
  filter(variable==2) %>% 
ggplot(aes(y=mean_mem_length,
             x=ntrtLong,
             fill=color_group))+
  geom_boxplot(alpha = 0.3, outlier.size = 0, size=0.3) + 
  geom_bar(stat = "identity", color = NA, size = 0) +
  geom_errorbar(aes(
    ymin = mean_mem_length - sd_mem_length,
    ymax = mean_mem_length + sd_mem_length,
     color = color_group
  ), width = 0.3, size = 0.3)+
    geom_hline(yintercept = 0, linetype = "dashed", color = "black") +
  scale_fill_manual(values = c("positive" = "#6A33C2",  # purple
                             "negative" = "#ff7f00")) + # orange
  scale_color_manual(values = c("positive" = "#6A33C2",  # purple
                             "negative" = "#ff7f00")) + # orange
  scale_shape_manual(values =c(21,24))+
  scale_y_continuous(breaks = c(6,3,0,-4,-8),
                     labels = function(y) format(y, nsmall = 1, digits = 1)) +
  coord_cartesian(ylim = c(-8,6), 
                  xlim = c(1,9),
                  clip = "off")+
  facet_grid(~dur, labeller = labeller(dur = c("1" = "All Years", "2" = "No Initial Response"))) +
  ylab("Difference in months when\nmemory length is >90%\n(mean ± sd)")+
  xlab("")+  
  geom_segment(data = filter(WEIGHTMoLength, dur == 1), 
               aes(x = 0.27, xend = 0.27, y = -8, yend = 6), inherit.aes = FALSE, color="gray20") +
  annotate("segment", y=-Inf, yend=-Inf, x=1, xend=9, color = "gray20") +
  annotate("segment", y=.5, yend=6, x=10, xend=10, color = "gray20") +
  annotate("segment", y=-.5, yend=-8, x=10, xend=10, color = "gray20") +
  geom_segment(data = filter(WEIGHTMoLength, dur == 2), 
               aes(x = 9.7, xend = 10, y = 6, yend = 6), inherit.aes = FALSE, color="gray20", linewidth=0.3)+
  geom_segment(data = filter(WEIGHTMoLength, dur == 2), 
               aes(x = 9.7, xend = 10, y = 0.5, yend = 0.5), inherit.aes = FALSE, color="gray20", linewidth=0.3)+
  geom_segment(data = filter(WEIGHTMoLength, dur == 2), 
               aes(x = 9.7, xend = 10, y = -0.5, yend = -0.5), inherit.aes = FALSE, color="gray20", linewidth=0.3)+
  geom_segment(data = filter(WEIGHTMoLength, dur == 2), 
               aes(x = 9.7, xend = 10, y = -8, yend = -8), inherit.aes = FALSE, color="gray20", linewidth=0.3)+
  annotate("text", x = 11.75, y = 6.75, label = "Longer\nMemory\nin:", color = "black", fontface = "bold", size = 3.5)+
  annotate("text", x = 11.75, y = 3.5, label = "\nINTACT\nplots", color = "gray30", fontface = "bold", size = 3.3)+
  annotate("text", x = 11.75, y = -4.5, label = "\nDISTURBED\nplots", color = "gray30", fontface = "bold", size = 3.3)+
  geom_text(data = filter(WEIGHTMoLength, dur == 1),
               aes(x = 2.5, y = 8.5), inherit.aes = FALSE, label = "Temperature", color = "black", size = 5, fontface = "bold")+
  theme_regular +
  theme(plot.margin = margin(t = 15, r = 75, b = 5, l = 5))

 final_b <- ggdraw(b) +
   draw_label("c)", x = 0.14, y = 0.939, size = 13, fontface = "bold", hjust = 0, vjust = 1)+
   draw_label("d)", x = 0.51, y = 0.939, size = 13, fontface = "bold", hjust = 0, vjust = 1) +
  # Rain cloud
  draw_image(image = icon_temp, x = -0.43, y = 0.45, scale = 0.080) +  # Panel A
  draw_label("†", x = 0.300, y = 0.470, size = 10, fontface = "bold", hjust = 0, vjust = 1, color = "#ffba76")
 
 final_b
```

Merge side-by-side plots - live biomass
```{r}
left_column <- plot_grid(final_a, final_b, ncol = 1)
left_column
ggsave(file.path(graph.wd,"EXTRA_Fig4_DiffMemoryLength_90_LiveBiomass.png"), plot = last_plot(), width=7, height=8, dpi = res_export, units="in")
```

## Supplement
###- [SI] Monthly weights
Creating dataset
```{r}

ntrt_dur <- tibble("dur" = rep(1:2, each=9),
                   "ntrt" = as.factor(rep(1:9, each=1, times=2)),
                   "ntrt_dur" = seq(1:18))

colntrt_faded <-  c(colntrt, "#80e9ca","#f4b57a","#c1adbd","#db9ac8","#cfab9f","#e2f07b","#fad36d","#e4c790","#b4b4b4")

WEIGHTMomodelpar2<- WEIGHTMomodelpar1 %>% 
  mutate(year = factor(ifelse(month<12, "y0", ifelse(month>12 & month<24,"y-1","y-2")), levels = c("y0","y-1","y-2")),
         # cat2 = ifelse(exp==1&dur==1, 1, ifelse(exp==2&dur==1, 3, ifelse(exp==1&dur==2, 2,4))),
         cat = ifelse(exp==1&dur==1, 1, ifelse(exp==2&dur==1, 2, ifelse(exp==1&dur==2, 3,4))),
         month_generic = ifelse(month %in% c(2,14,26),1, ifelse(month %in% c(5,17,29),2,
                                                                ifelse(month %in% c(8,20,32), 3, 4)))) %>% 
  left_join(ntrt_dur)

# define how much to dodge
dodge_width <- 0.8

# define position of some features within the graph
xy_values_icon <- list(
  Var1 = list("x_icon" = -0.475, "y_icon" =  0.474, "icon" = icon_rain, "ylim" = 0.17, "icon_scale" = 0.03), 
  Var2 = list("x_icon" = -0.475, "y_icon" =  0.474, "icon" = icon_temp, "ylim" = 0.19, "icon_scale" = 0.04),
  Var3 = list("x_icon" = -0.475, "y_icon" =  0.474, "icon" = icon_rain, "ylim" = 0.23, "icon_scale" = 0.03), 
  Var4 = list("x_icon" = -0.475, "y_icon" =  0.474, "icon" = icon_temp, "ylim" = 0.21, "icon_scale" = 0.04)
)

temp_df <- data.frame(
  cat = "4",
  x = c(seq(0.74, 9, by = 1), seq(1, 9, by = 1), seq(1.26, 10, by = 1)),
  y = -0.03,  # offset y1 lower
  label = rep(c("y0", "y-1", "y-2"), each = 9)
)

```

Plots
```{r}
#ribbons linking monthly error bars (Months and Years)
for (Var in 1:nrow(summaryVar)) { # as only 2 graphs are going to be generated here

  current_xy_values <- xy_values_icon[[Var]]

a <-
  WEIGHTMomodelpar2 %>% 
  filter(variable==summaryVar[Var,6],
         biomass== summaryVar[Var,4]) %>% 
  ggplot(aes(x=ntrtLong,y=`statistics.Mean`,
             color=as.factor(ntrt_dur),
             group=month
             ))+
  geom_errorbar(aes(ymin=`quantiles.2.5.`, ymax=`quantiles.97.5.`), 
                show.legend = FALSE,
                width=0.2,
                linewidth=0.5, 
                alpha=0.5,
                position=position_dodge(width=dodge_width))+
  geom_point(aes(shape=as.factor(month_generic),
                 fill=as.factor(cat),
                 size = as.factor(month_generic)),
             position=position_dodge(width=dodge_width)
             )+
    scale_size_manual(values = c("1" = 2.5, "2" = 2.5, "3" = 2.5, "4" = 3.5),
                     labels = c("D-O fall", "S-J late GS", "J-A early GS", "M-J winter"),
                     name = "Seasons")+
    scale_color_manual(values = colntrt_faded,
                     labels = c("0 + None","0 + All","1 + All","2 + All",
                                "3.4 + All","5.4 + All","9.5 + All","17 + All","27.2 + All",
                                "","","","","","","","",""),
                     name = "Nutrient levels")+
  scale_fill_manual(values = c("1" = 1, "2" = 2),  # use only the levels you want
  labels = c("1" = "All years", "2" = "Without initial\nresponse"),
                    name = "Community type"
                    )+
  scale_shape_manual(values = c(19,17,15,18),
                     labels = c("D-O fall", "S-J late GS", "J-A early GS", "M-J winter"),
                     name = "Seasons"
                     )+
  coord_cartesian(ylim =c(0, current_xy_values$ylim), clip = "off")+
    facet_wrap(~cat, nrow=4,
               labeller = labeller(cat = c("1" = "Intact", "3" = "Intact: without initial response ", "2" = "Disturbed", "4" = "Disturbed: without initial response ")))+
  ylab(paste0("Monthly importance weights of ",summaryVar[Var,3],"\n (posterior mean ± 95% CIs)"))+
    xlab(NULL)+
  theme_facet + #pre-defined themes for facet graphs
  theme(legend.position = "right",
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
          plot.margin = margin(t = 5, r = 5, b = 20, l = 5)) +
  guides(shape = guide_legend(override.aes = list(alpha=1,size=4)),
         fill = guide_legend(override.aes = list(alpha=1,size=4, shape=c(19,19),color=c("black","gray70"))),
         color = guide_legend(override.aes = list(alpha=1,size=4, shape=19, color=c(colntrt[9], colntrt[1:8],
                                                                             NA,NA,NA,NA,NA,NA,NA,NA,NA))))+
  annotate("segment", y=0, yend=current_xy_values$ylim, x=-Inf, xend=-Inf, color = "gray20")+
  geom_text(data = temp_df,
          aes(x = x, y = y, label = label),
          inherit.aes = FALSE,
          color = "gray30",
          fontface = "bold",
          size = 3.5)+
  geom_segment(data = temp_df,
             aes(x = x - 0.1, xend = x + 0.1, y = y + 0.015, yend = y + 0.015),
             inherit.aes = FALSE,
             color = "black",
             linewidth = 1)+
geom_segment(data = data.frame(x = seq(0.865, 9, by = 1)),
             aes(x = x, xend = x, y = 0, yend = current_xy_values$ylim),
             color = "gray", linetype = "dashed",
             inherit.aes = FALSE) +
geom_segment(data = data.frame(x = seq(1.13, 10, by = 1)),
             aes(x = x, xend = x, y = 0, yend = current_xy_values$ylim),
             color = "gray", linetype = "dashed",
             inherit.aes = FALSE)

final_a <- ggdraw(a) +
  # Rain cloud
  draw_image(image = current_xy_values$icon, x = current_xy_values$x_icon, y =  current_xy_values$y_icon, scale = current_xy_values$icon_scale) +
  draw_label("a)", x = 0.053, y = 0.986, size = 15, fontface = "bold", hjust = 0, vjust = 1) +
  draw_label("b)", x = 0.053, y = 0.746, size = 15, fontface = "bold", hjust = 0, vjust = 1) +
  draw_label("c)", x = 0.053, y = 0.506, size = 15, fontface = "bold", hjust = 0, vjust = 1) +
  draw_label("d)", x = 0.053, y = 0.266, size = 15, fontface = "bold", hjust = 0, vjust = 1) +
  draw_label("†", x = 0.471, y = 0.700, size = 15, fontface = "bold", hjust = 0, vjust = 1, color = "#BC4399")
final_a

# saves
    ggsave(paste0(file.path(graph.wd),"/FigSX_MonthlyWeight_",summaryVar[Var,1],"_",summaryVar[Var,5],".png"), plot = last_plot(), width=15, height=8, dpi = res_export, units="in")
    
}
```

###- [SI] Cumulative weights
Creating dataset - live biomass
```{r}
cumulativeWeight <- WEIGHTMomodelpar %>%
  group_by(dur, exp, ntrt, variable) %>%
  arrange(exp, ntrt, variable, month) %>%
  mutate(cumulative_sum = cumsum(statistics.Mean),
         shape=ifelse(exp==1,16,19))
```

Plot: Precipitation - live biomass
```{r}
#SEASONS
a<-cumulativeWeight %>% 
  filter(variable==1) %>% 
  filter(ntrt %in% c(1,8)) %>% 
  ggplot(aes(x=month, y=cumulative_sum, color=as.factor(ntrt)))+
  annotate("rect", xmin = 3.5, xmax = 9.5, ymin = -Inf, ymax = Inf, alpha = .05) +
  annotate("rect", xmin = 15.5, xmax = 21.5, ymin = -Inf, ymax = Inf, alpha = .05) +
  annotate("rect", xmin = 27.5, xmax = 33.5, ymin = -Inf, ymax = Inf, alpha = .05) +
  geom_vline(xintercept = seq(3.5, 36, by = 3), color = "gray", linetype = "dashed") +
  geom_vline(xintercept = seq(12.5, 36, by = 12), color = "gray50") +
  geom_point(aes(shape = as.factor(exp)), size=4, alpha=0.5) +
  geom_hline(yintercept = 0.5, linetype = "dotted", color = "gray5")+
  geom_hline(yintercept = 0.75, linetype = "dotted", color = "gray5")+
  geom_hline(yintercept = 0.90, linetype = "dotted", color = "gray5")+
  scale_color_manual(values = c(colntrt[1],colntrt[8]),labels = c("0 + All","27.2 + All")) +
  facet_wrap(~dur, nrow=2, #scales = "free_y",
             labeller = labeller(dur = c("1" = "Precipitation: All Years", "2" = "Precipitation: Without Initial Response"))) +
  scale_shape_manual(values = c(16, 17),labels = c("Intact", "Disturbed"))+
  scale_x_continuous(expand = c(0.01,0),
                       breaks = seq(2,36, by=3)) +
  coord_cartesian(ylim = c(0,1), 
                    xlim=c(0.5,36), clip = "off")+
  ylab("Cumulative memory weight")+
  theme_facet2 + 
  theme(legend.margin=margin(0,0,0,0),
        legend.position = c(0.93,0.15),
        legend.text = element_text(size=8),
        legend.title = element_blank(),
        legend.spacing = unit(0, "cm"),
        # axis.text = element_text(size = 12),
        axis.title.x = element_blank(),
        axis.text.x = element_blank(),
        axis.title = element_text(size = 12, face = "bold"),
        # axis.title.x = element_blank(),
        strip.text = element_text(face = "bold", size = 11),
        plot.margin = margin(t = 5, r = 5, b = 5, l = 5),
        legend.key = element_blank(),
        legend.background = element_rect(fill = "white", color = NA)) +
  guides(shape = guide_legend(override.aes = list(shape=c(19,17),alpha=1, size=3.5)),
         color = guide_legend(override.aes = list(size=4, shape=c(15)))) +
  geom_segment(data = filter(cumulativeWeight), 
               aes(x = 0.14, xend = 0.14, y = 0, yend = 1), inherit.aes = FALSE, color="gray20") +
  geom_segment(data = filter(cumulativeWeight, variable == 2), 
               aes(x = 1, xend = 36, y = -Inf, yend = -Inf), inherit.aes = FALSE, color="gray20")+
  annotate("text", x = 4, y = 0.53, label = "50% memory", color = "gray5", fontface = "bold", size = 3.5) +
  annotate("text", x = 4, y = 0.77, label = "75% memory", color = "gray5", fontface = "bold", size = 3.5)+
  annotate("text", x = 4, y = 0.93, label = "90% memory", color = "gray5", fontface = "bold", size = 3.5) 

final_a <- ggdraw(a) +
  draw_label("a)", x = 0.095, y = 0.976, size = 15, fontface = "bold", hjust = 0, vjust = 1) +
  draw_label("b)", x = 0.095, y = 0.486, size = 15, fontface = "bold", hjust = 0, vjust = 1) +
  # Rain cloud
  draw_image(image = icon_rain, x = -0.447, y = 0.46, scale = 0.040) 
 
 final_a
```

Plot: Temperature - live biomass
```{r}
#SEASONS
b<-cumulativeWeight %>% 
  filter(variable==2) %>% 
  filter(ntrt %in% c(1,8)) %>% 
  ggplot(aes(x=month, y=cumulative_sum, color=as.factor(ntrt)))+
  annotate("rect", xmin = 3.5, xmax = 9.5, ymin = -Inf, ymax = Inf, alpha = .05) +
  annotate("rect", xmin = 15.5, xmax = 21.5, ymin = -Inf, ymax = Inf, alpha = .05) +
  annotate("rect", xmin = 27.5, xmax = 33.5, ymin = -Inf, ymax = Inf, alpha = .05) +
  geom_vline(xintercept = seq(3.5, 36, by = 3), color = "gray", linetype = "dashed") +
  geom_vline(xintercept = seq(12.5, 36, by = 12), color = "gray50") +
  geom_point(aes(shape = as.factor(exp)), size=4, alpha=0.5) +
  geom_hline(yintercept = 0.5, linetype = "dotted", color = "gray5")+
  geom_hline(yintercept = 0.75, linetype = "dotted", color = "gray5")+
  geom_hline(yintercept = 0.90, linetype = "dotted", color = "gray5")+
  scale_color_manual(values = c(colntrt[1],colntrt[8]),labels = c("0 + All","27.2 + All")) +
  facet_wrap(~dur, nrow=2, #scales = "free_y",
             labeller = labeller(dur = c("1" = "Temperature: All Years", "2" = "Temperature: Without Initial Response"))) +
  scale_shape_manual(values = c(16, 17),labels = c("Intact", "Disturbed"))+
  scale_x_continuous(expand = c(0.01,0),
                       breaks = seq(2,36, by=3),
                       labels = rep(c("D-O\nfall","S-J\nlate\nGS","J-A\nearly\nGS","M-J\nwinter"), times=3)) +
  coord_cartesian(ylim = c(0,1), 
                    xlim=c(0.5,36), clip = "off")+
  ylab("Cumulative memory weight")+
  theme_facet2 + 
  theme(legend.margin=margin(0,0,0,0),
        legend.position = c(0.93,0.15),
        legend.text = element_text(size=8),
        legend.title = element_blank(),
        legend.spacing = unit(0, "cm"),
        axis.title.x = element_blank(),
        axis.title = element_text(size = 12, face = "bold"),
        strip.text = element_text(face = "bold", size = 11),
        plot.margin = margin(t = 5, r = 5, b = 10, l = 5),
        legend.key = element_blank(),
        legend.background = element_rect(fill = "white", color = NA)) +
  guides(shape = guide_legend(override.aes = list(shape=c(19,17),alpha=1, size=3.5)),
         color = guide_legend(override.aes = list(size=4, shape=c(15)))) +
  geom_segment(data = filter(cumulativeWeight), 
               aes(x = 0.14, xend = 0.14, y = 0, yend = 1), inherit.aes = FALSE, color="gray20") +
  geom_segment(data = filter(cumulativeWeight, variable == 2), 
               aes(x = 1, xend = 36, y = -Inf, yend = -Inf), inherit.aes = FALSE, color="gray20")+
  annotate("text", x = 4, y = 0.53, label = "50% memory", color = "gray5", fontface = "bold", size = 3.5) +
  annotate("text", x = 4, y = 0.77, label = "75% memory", color = "gray5", fontface = "bold", size = 3.5)+
  annotate("text", x = 4, y = 0.93, label = "90% memory", color = "gray5", fontface = "bold", size = 3.5) +
  annotate("text", x = 6.5, y = -0.28, label = "y0", color = "gray30", fontface = "bold", size = 3.5) +
  annotate("text", x = 18.5, y = -0.28, label = "y-1", color = "gray30", fontface = "bold", size = 3.5) + 
  annotate("text", x = 30.5, y = -0.28, label = "y-2", color = "gray30", fontface = "bold", size = 3.5)

final_b <- ggdraw(b) +
  draw_label("c)", x = 0.095, y = 0.976, size = 15, fontface = "bold", hjust = 0, vjust = 1) +
  draw_label("d)", x = 0.095, y = 0.526, size = 15, fontface = "bold", hjust = 0, vjust = 1) +
  # Temp thermometer
  draw_image(image = icon_temp, x = -0.440, y = 0.46, scale = 0.040) 

 final_b
```

Merge plots
```{r}
left_column <- plot_grid(final_a, final_b, ncol = 1)
left_column
ggsave(file.path(graph.wd,"FigSZ_CumulativeWeight_Seasons_LiveBiomass.png"), plot = last_plot(), width=7, height=10, dpi = res_export, units="in")
```

###- [SI] Yearly weights
Creating dataset - live biomass
```{r}
#dataframe
WEIGHTYrmodelpar<- parameters_All %>% 
  filter(grepl("^yr.w",parameter)) %>% 
  mutate(ntrt = factor(rep(1:9,times=24, each=1), levels = order_levels),
         ntrtLong = factor(rep(c("0 + All", "1 + All", "2 + All", "3.4 + All", "5.4 + All", "9.5 + All", "17 + All", "27.2 + All", "0 + None"), times=24, each=1), levels = ntrtLong_levels),
         year = rep(0:2,times=8, each=9),
         variable = rep(1:2,times=4, each=27),
         month = rep(c(6.5,18.5,30.5),times=8, each=9),
         cat = ifelse(exp==1&dur==1, 1, ifelse(exp==2&dur==1, 2, ifelse(exp==1&dur==2, 3,4))))

WEIGHTYrmodelpar1 <- WEIGHTYrmodelpar %>% 
  mutate(year = factor(ifelse(month==6.5, "y0", ifelse(month==18.5,"y-1","y-2")), levels = c("y0","y-1","y-2")),
         cat2 = ifelse(exp==1&dur==1, 1, ifelse(exp==2&dur==1, 3, ifelse(exp==1&dur==2, 2,4))))

# define how much to dodge
dodge_width <- 0.5

# define position of some features within the graph
xy_values_icon <- list(
  Var1 = list("x_icon" = -0.45, "y_icon" =  0.474, "icon" = icon_rain, "ylim" = 0.7, "letter" = "a)"), 
  Var2 = list("x_icon" = -0.44, "y_icon" =  0.474, "icon" = icon_temp, "ylim" = 0.8, "letter" = "b)")
)
```

Plot: Precipitation - live biomass
```{r}
#ribbons linking monthly error bars (Months and Years)
# for (Var in 1:(nrow(summaryVar)-2)) { # as only 2 graphs are going to be generated here
Var <- 1

current_xy_values <- xy_values_icon[[Var]]

a <- WEIGHTYrmodelpar1 %>% 
  filter(variable==Var) %>% 
  ggplot(aes(x=ntrtLong,y=`statistics.Mean`,
             color=as.factor(cat),
             group=month
             ))+
  geom_hline(yintercept = 0, linetype = "dashed", color = "darkgray")+
  geom_errorbar(aes(ymin=`quantiles.2.5.`, ymax=`quantiles.97.5.`),
                width=0.3,
                linewidth=0.7, 
                position=position_dodge(width=dodge_width))+
  geom_point(aes(shape=as.factor(year),
                 fill=as.factor(cat)),
                 size=3,
             position=position_dodge(width=dodge_width)
             )+
  scale_color_manual(values = c(pals::cols25(5)[4], pals::cols25(5)[5],"#ab8ae0","#ffba76"))+
  scale_fill_manual(values = c(1:4),
                    labels = c("Intact","Intact\nno initial", "Disturbed","Disturbed\nno transient"))+
  scale_shape_manual(values = c(19,17,15),
                     labels = c("Current year", "Year -1", "Year -2"))+
  coord_cartesian(ylim =c(0, current_xy_values$ylim), clip = "off")+
    facet_wrap(~cat, nrow=4,labeller = labeller(cat = c("1" = "Intact", "3" = "Intact: without initial response ", "2" = "Disturbed", "4" = "Disturbed: without initial response ")))+
  ylab(paste0("Yearly importance weights of ",summaryVar[Var,3],"\n (posterior mean ± 95% CIs)"))+
    xlab(NULL)+
  theme_facet + #pre-defined themes for facet graphs
  theme(legend.position = "none",
        axis.text.x = element_text(size=10),
          plot.margin = margin(t = 5, r = 5, b = 25, l = 5)) +
  annotate("segment", y=0, yend=current_xy_values$ylim, x=-Inf, xend=-Inf, color = "gray20")+
  geom_segment(data = filter(WEIGHTYrmodelpar1, cat2==4), 
               aes(x = 1, xend = 9, y = -Inf, yend = -Inf), inherit.aes = FALSE, color="gray20")

final_a <- ggdraw(a) +
  # Rain cloud
  draw_image(image = current_xy_values$icon, x = current_xy_values$x_icon, y =  current_xy_values$y_icon, scale = 0.04) +
  draw_label("a)", x = 0.1, y = 0.984, size = 14, fontface = "bold", hjust = 0, vjust = 1) +
  draw_label("b)", x = 0.1, y = 0.752, size = 14, fontface = "bold", hjust = 0, vjust = 1) +
  draw_label("c)", x = 0.1, y = 0.521, size = 14, fontface = "bold", hjust = 0, vjust = 1) +
  draw_label("d)", x = 0.1, y = 0.290, size = 14, fontface = "bold", hjust = 0, vjust = 1) +
  draw_label("*", x = 0.53, y = 0.718, size = 18, fontface = "bold", hjust = 0, vjust = 1)
final_a
```

Plot: Temperature - live biomass
```{r}
## Temperature
Var <- 2

current_xy_values <- xy_values_icon[[Var]]

b <- WEIGHTYrmodelpar1 %>% 
  filter(variable==Var) %>% 
  ggplot(aes(x=ntrtLong,y=`statistics.Mean`,
             color=as.factor(cat),
             group=month
             ))+
  geom_hline(yintercept = 0, linetype = "dashed", color = "darkgray")+
  geom_errorbar(aes(ymin=`quantiles.2.5.`, ymax=`quantiles.97.5.`),
                width=0.3,
                linewidth=0.7, 
                position=position_dodge(width=dodge_width))+
  geom_point(aes(shape=as.factor(year),
                 fill=as.factor(cat)),
                 size=3,
             position=position_dodge(width=dodge_width)
             )+
  scale_color_manual(values = c(pals::cols25(5)[4], pals::cols25(5)[5],"#ab8ae0","#ffba76"))+
  scale_fill_manual(values = c(1:4),
                    labels = c("Intact","Intact\nno initial response", "Disturbed","Disturbed\nno initial response"))+
  scale_shape_manual(values = c(19,17,15),
                     labels = c("Current year  ", "Year -1", "Year -2"))+
  coord_cartesian(ylim =c(0, current_xy_values$ylim), clip = "off")+
    facet_wrap(~cat, nrow=4,labeller = labeller(cat = c("1" = "Intact", "3" = "Intact: without initial response ", "2" = "Disturbed", "4" = "Disturbed: without initial response ")))+
  ylab(paste0("Yearly importance weights of ",summaryVar[Var,3],"\n (posterior mean ± 95% CIs)"))+
    xlab(NULL)+
  theme_facet + #pre-defined themes for facet graphs
  theme(legend.position = "bottom",
        legend.title = element_blank(),
        legend.text = element_text(size=10),
        legend.margin = margin(t=-5,r=5,b=1,l=-5),
        axis.text.x = element_text(size=10),
          plot.margin = margin(t = 5, r = 5, b = 0, l = 5)) +
  guides(shape = guide_legend(override.aes = list(alpha=1,size=4)),
         fill = "none",
         color = "none")+
  annotate("segment", y=0, yend=current_xy_values$ylim, x=-Inf, xend=-Inf, color = "gray20")+
  geom_segment(data = filter(WEIGHTYrmodelpar1, cat2==4), 
               aes(x = 1, xend = 9, y = -Inf, yend = -Inf), inherit.aes = FALSE, color="gray20")

final_b <- ggdraw(b) +
  # Rain cloud
  draw_image(image = current_xy_values$icon, x = current_xy_values$x_icon, y =  current_xy_values$y_icon, scale = 0.035) +
  draw_label("e)", x = 0.1, y = 0.984, size = 14, fontface = "bold", hjust = 0, vjust = 1) +
  draw_label("f)", x = 0.1, y = 0.752, size = 14, fontface = "bold", hjust = 0, vjust = 1) +
  draw_label("g)", x = 0.1, y = 0.523, size = 14, fontface = "bold", hjust = 0, vjust = 1) +
  draw_label("h)", x = 0.1, y = 0.288, size = 14, fontface = "bold", hjust = 0, vjust = 1) +
  draw_label("*", x = 0.53, y = 0.710, size = 18, fontface = "bold", hjust = 0, vjust = 1)
final_b
```

Merge plots - live biomass
```{r}
left_column <- plot_grid(final_a, final_b, ncol = 2, rel_widths = c(1, 1))
left_column
ggsave(file.path(graph.wd,"FigSY_YearWeight_LiveBiomass.png"), plot = last_plot(), width=15, height=7, dpi = res_export, units="in")
```


###- [SI] Standardized Global effects
Creating 4 independent plots
```{r}
Globalmodelpar<- parameters_All %>% 
  filter(grepl("^mu_a.star\\[\\d+\\]$",parameter)) %>% 
  mutate(alpha = rep(2:3,times=4),
         filling=ifelse(`quantiles.2.5.`<0&`quantiles.97.5.`<0|                                                              `quantiles.2.5.`>0&`quantiles.97.5.`>0, "black","white"),
         filling = ifelse(exp==1&dur==1, "black", filling),
         shape=ifelse(exp==1&dur==1,21,
                      ifelse(exp==2&dur==1,21,22))) %>% 
  mutate(statistics.Mean = ifelse(alpha==1, statistics.Mean*clim.means$Precip_mm, statistics.Mean*clim.means$MaxTemp_C),
         quantiles.2.5. = ifelse(alpha==1, quantiles.2.5.*clim.means$Precip_mm, quantiles.2.5.*clim.means$MaxTemp_C),
         quantiles.97.5. = ifelse(alpha==1, quantiles.97.5.*clim.means$Precip_mm, quantiles.97.5.*clim.means$MaxTemp_C)) 
dodge_width <- 0.5



a<-
  Globalmodelpar %>% 
  filter(alpha==2 & biomass==1) %>% 
  ggplot(aes(x=exp,y=`statistics.Mean`,
             group=dur
             ))+
  geom_hline(yintercept = 0, linetype = "dashed", color = "darkgray")+
  geom_errorbar(aes(ymin=`quantiles.2.5.`, ymax=`quantiles.97.5.`),
                width=0.3,
                linewidth=0.7, 
                position=position_dodge(width=dodge_width))+
  geom_point(aes(shape=as.factor(shape),
                 fill=as.factor(filling)),
                 size=3,
             position=position_dodge(width=dodge_width)
             )+
  scale_shape_manual(values = c(21,22),
                     labels = c("All years","Without transient\n community")) +
  scale_fill_manual(values = c("black","white")) +
  ylab("Standardized coefficient\neffects on live biomass \n(posterior mean ± 95% CIs)")+
  xlab(NULL)+
 
  scale_x_continuous(breaks = c(1,2),
                     labels = c("Intact","Disturbed")) +
  coord_cartesian(#ylim = c(-400, 1400), 
                    xlim=c(0.5,2.5), 
                  clip = "off") +
  scale_y_continuous(n.breaks = 8) +
  geom_segment(data = filter(Globalmodelpar, alpha == "2", biomass==1),
               aes(x = 0.378, xend = 0.378,
                   y = 0,
                   yend = 140), inherit.aes = FALSE, color="gray20") +
  ggtitle("Precipitation")+
  theme_facet +
  theme(legend.position = "none",
        legend.title = element_blank(),
        legend.margin = margin(1,5,1,-5),
        legend.key.size = unit(0.3, "cm"),
        legend.text = element_text(size=rel(0.6)),
        axis.text.x = element_text(size = 12),
        axis.text.y = element_text(size = 12),
        axis.title.y = element_text(margin = margin(r = 10)),
        plot.margin = margin(t = 5, r = 5, b = 5, l = 5),
        plot.title = element_text(face = "bold", hjust = 0.5, size = 14)) +
  guides(shape = guide_legend(override.aes = list(alpha=1,size=2,
                                                  shape=c(19,17),
                                                  color=c("black","black"))),
         fill = "none")

b<-
  Globalmodelpar %>% 
  filter(alpha==3 & biomass==1) %>% 
  ggplot(aes(x=exp,y=`statistics.Mean`,
             group=dur
             ))+
  geom_hline(yintercept = 0, linetype = "dashed", color = "darkgray")+
  geom_errorbar(aes(ymin=`quantiles.2.5.`, ymax=`quantiles.97.5.`),
                width=0.3,
                linewidth=0.7, 
                position=position_dodge(width=dodge_width))+
  geom_point(aes(shape=as.factor(shape),
                 fill=as.factor(filling)),
                 size=3,
             position=position_dodge(width=dodge_width)
             )+
  scale_shape_manual(values = c(21,22),
                     labels = c("All years","Without transient\n community")) +
  scale_fill_manual(values = c("black","white")) +
  ylab("Standardized coefficient\neffects on live biomass \n(posterior mean ± 95% CIs)")+
  xlab(NULL)+
 
  scale_x_continuous(breaks = c(1,2),
                     labels = c("Intact","Disturbed")) +
  coord_cartesian(#ylim = c(-400, 1400), 
                    xlim=c(0.5,2.5), 
                  clip = "off") +
  scale_y_continuous(n.breaks = 8) +
  geom_segment(data = filter(Globalmodelpar, alpha == "2", biomass==1),
               aes(x = 0.378, xend = 0.378,
                   y = -250,
                   yend = 1250), inherit.aes = FALSE, color="gray20") +
  ggtitle("Temperature")+
 theme_facet +
  theme(legend.position = "none",
        legend.title = element_blank(),
        legend.margin = margin(1,5,1,-5),
        legend.key.size = unit(0.3, "cm"),
        legend.text = element_text(size=rel(0.6)),
        axis.text.x = element_text(size = 12),
        # axis.ticks.x = element_blank(),
         axis.title.y = element_blank(),
        axis.text.y = element_text(size = 12),
        plot.margin = margin(t = 5, r = 5, b = 5, l = 5),
        plot.title = element_text(face = "bold", hjust = 0.5, size = 14)) +
  guides(shape = guide_legend(override.aes = list(alpha=1,size=2,
                                                  shape=c(19,17),
                                                  color=c("black","black"))),
         fill = "none")

final_a <- ggdraw(a) +
  draw_label("a)", x = 0.270, y = 0.850, size = 10, fontface = "bold", hjust = 0, vjust = 1)
final_a

final_b <- ggdraw(b) +
  draw_label("b)", x = 0.165, y = 0.850, size = 10, fontface = "bold", hjust = 0, vjust = 1)

```

Merge plots
```{r}
top_row <- plot_grid(final_a, final_b,
                         ncol = 2, nrow=1, rel_widths = c(1, 0.94),
                     align = "h", 
                     axis = "tb")

top_row

ggsave(file.path(graph.wd,"FigSW_StdGlobalCoefs.png"), plot = last_plot(), width=8, height=3, dpi = res_export, units="in")
```

